# Frail Elderly Cohort (high frailty)

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")

source("R/general.R")
source("R/descriptive_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")

options(scipen = 999)
```

This cohort includes elderly patients with a high level of frailty, specifically, those 75 years of age or over with an emergency admission and a frailty score over 15. The frailty score is calculated from ICD-10 diagnoses recorded for admissions during the previous 2 years and using the risk scores in Gilbert et al (2018), Development and validation of a Hospital Frailty Risk Score focusing on older people in acute care settings using electronic hospital records: an observational study. The Lancet, 391(10132), pp.1775-1782.


## Descriptive Analysis of Mitigable Activity

```{r}
#| label: tbl-perc_frail
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24.
targets::tar_read(total_beddays_episodes_frail) |>
  get_table_perc()
```

### Patient Characteristics

::: panel-tabset

### Age

::: panel-tabset

#### Perc

```{r}
#| label: tbl-perc_frail_age
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by age.
targets::tar_read(perc_spells_frail_age) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_frail_age
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by age.
targets::tar_read(perc_spells_frail_age) |>
  get_perc_spells_by_group_plot("age_range")
```

#### Rates per 100,000

```{r}
#| label: tbl-rate_frail_age
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by age.
targets::tar_read(rates_per_pop_age_frail) |>
  get_rates_per_pop_table() 
```

```{r}
#| label: fig-rate_frail_age
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by age.
targets::tar_read(rates_per_pop_age_frail) |>
  get_rates_per_pop_plot("age_range")
```

:::

### Ethnicity

::: panel-tabset

#### Perc

```{r}
#| label: tbl-perc_frail_ethnicity
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by ethnic category.
targets::tar_read(perc_spells_frail_ethnicity) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_frail_ethnicity
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by ethnic category.
targets::tar_read(perc_spells_frail_ethnicity) |>
  get_perc_spells_by_group_plot("Ethnic_Category")
```

#### Rates per 100,000

```{r}
#| label: tbl-rate_frail_ethnicity
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by ethnic category.
targets::tar_read(rates_per_pop_ethnicity_frail) |>
  get_rates_per_pop_table() 
```

```{r}
#| label: fig-rate_frail_ethnicity
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by ethnic category.
targets::tar_read(rates_per_pop_ethnicity_frail) |>
  get_rates_per_pop_plot("Ethnic_Category")
```

:::

### IMD

::: panel-tabset

#### Perc


```{r}
#| label: tbl-perc_frail_imd
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by IMD decile.
targets::tar_read(perc_spells_frail_imd) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_frail_imd
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by IMD decile.
targets::tar_read(perc_spells_frail_imd) |>
  dplyr::mutate(imd19_decile = factor(imd19_decile)) |>
  get_perc_spells_by_group_plot("imd19_decile")
```

#### Rates per 100,000

```{r}
#| label: tbl-rate_frail_imd
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by IMD decile.
targets::tar_read(rates_per_pop_imd_frail) |>
  get_rates_per_pop_table() 
```

```{r}
#| label: fig-rate_frail_imd
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by IMD decile.
targets::tar_read(rates_per_pop_imd_frail) |>
  get_rates_per_pop_plot("imd19_decile")
```

:::

### Sex

::: panel-tabset

#### Perc


```{r}
#| label: tbl-perc_frail_sex
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by sex.
targets::tar_read(perc_spells_frail_sex) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_frail_sex
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by sex.
targets::tar_read(perc_spells_frail_sex) |>
  get_perc_spells_by_group_plot("sex")
```

#### Rates per 100,000

```{r}
#| label: tbl-rate_frail_sex
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by sex.
targets::tar_read(rates_per_pop_sex_frail) |>
  get_rates_per_pop_table() 
```

```{r}
#| label: fig-rate_frail_sex
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by sex.
targets::tar_read(rates_per_pop_sex_frail) |>
  get_rates_per_pop_plot("sex")
```

:::

:::

### LOS

```{r}
#| label: tbl-perc_frail_los
#| tbl-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by length of stay.
targets::tar_read(perc_spells_frail_los) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_frail_los
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by length of stay.
targets::tar_read(perc_spells_frail_los) |>
  get_perc_spells_by_group_plot("los_range")
```

### Specialty

```{r}
#| label: tbl-perc_frail_mainspecf
#| tbl-cap: Top 10 specialties of mitigable activity for Frail and Elderly Admissions in 2023-24.
specialty_key <- targets::tar_read(specialty_key) |>
  dplyr::rename(specialty = main_specialty_title,
                specialty_group = group)

frail_specialties <- targets::tar_read(perc_spells_frail_mainspef) |>
  dplyr::left_join(specialty_key, by = c("mainspef" = "dd_code"))

frail_specialties |>
  dplyr::arrange(desc(spells)) |>
  dplyr::slice(1:10) |>
  dplyr::select(specialty, spells, perc) |>
  get_table_perc() 
```

## Cohort overlap

### Number and proportion within multiple other cohorts
This gives the number and proportion of the Frail Elderly High admissions/beddays that are included in other multiple mitigatable cohorts. Due to the definition of this mitigator all of those in this cohort are also in the Emergency Elderly cohort, and therefore the number included in no other cohorts is zero. One quarter of this cohort are included 5 or more additional mitigator cohorts.

::: panel-tabset

#### Admissions
```{r, fig.width=4, fig.height=4}
#| label: fig-number_of_cohorts_spells
#| fig-cap: The number and percentage of mitigator cohorts that the Frail Elderly spells are a part of (2023/24).

total_cohort_numbers<-targets::tar_read(total_cohort_numbers)|>
  filter(frail_elderly_high==1)


plotting_barchart_number_of_cohorts(total_cohort_numbers, episodes)
```


#### Beddays
```{r, fig.width=4, fig.height=4}
#| label: fig-number_of_cohorts_beddays
#| fig-cap: The number and percentage of mitigator cohorts that the Frail Elderly beddays are a part of (2023/24).

plotting_barchart_number_of_cohorts(total_cohort_numbers, beddays)
```

:::



### Inclusion within other mitigatable activity cohorts
This shows whether the activity within the Elderly Frail High activity is also included in other mitigator cohorts, including the number and precentage of Elderly Frail High activity that is also within the other mitigator cohorts. For example, Elderly Frail High cohort  overlaps with nearly all of the other mitigator cohorts, all the Elderly Frail High cohort activity is also included in the Emergency Elderly cohort, and 63% of this cohort are in the Alcohol Partially Attributable Chronic cohort.

::: panel-tabset

#### Admissions
```{r, fig.width=10, fig.height=6 }
#| label: fig-prop_other_cohorts_frail_spells
#| fig-cap: The number and proportion of Frail Elderly spells that are included in each of the other cohorts (2023/24).

plotting_barchart_summary_of_overlaps(total_cohort_numbers,"frail_elderly_high", episodes)

```

#### Beddays
```{r, fig.width=10, fig.height=6 }
#| label: fig-prop_other_cohorts_frail_beddays
#| fig-cap: The number and proportion of Frail Elderly beddays that are included in each of the other cohorts (2023/24).


plotting_barchart_summary_of_overlaps(total_cohort_numbers,"frail_elderly_high", beddays)

```
:::


### Most common cohort overlaps
These are the most common cohort combinations for the Elderly Frail High cohort. For this cohort there are a very large number of different cohort combinations, so there are many smaller size cohort combinations that are not shown (all combinations together would add to 100%).

::: panel-tabset

#### Admissions
```{r, fig.width=10, fig.height=6}
#| label: fig-upset_plot_frail_spells
#| fig-cap: The 15 most common mitigator cohort overlaps for Frail Elderly spells (2023/24).
plot_upset_plot(total_cohort_numbers, episodes)

```

#### Beddays
```{r, fig.width=10, fig.height=6}
#| label: fig-upset_plot_frail_beddays
#| fig-cap: The 15 most common mitigator cohort overlaps for Frail Elderly beddays (2023/24).
plot_upset_plot(total_cohort_numbers, beddays)

```

:::





## Trend Analysis

### England

::: panel-tabset
#### Number over time
::: panel-tabset

#### Admissions
```{r, fig.width=8, fig.height=4}
#| label: fig-number_trends_spells_england
#| fig-cap: The total number of admissions for the Frail Elderly High mitigatable activity cohort in England over the last 10 years. 
numbers_over_time<-tar_read(numbers_over_time)

plot_of_number_over_time(numbers_over_time, "frail_elderly_high", episodes)

```
#### Beddays

```{r, fig.width=8, fig.height=4}
#| label: fig-number_trends_beddays_england
#| fig-cap: The total number of beddays for the Frail Elderly High mitigatable activity cohort in England over the last 10 years. 
plot_of_number_over_time(numbers_over_time, "frail_elderly_high", beddays)

```
:::

#### By proportion of emergency activity 
::: panel-tabset
#### Admissions
```{r, fig.width=8, fig.height=4}
#| label: fig-percent_trends_spells_england
#| fig-cap: The percentage of total emergency admissions that are for Frail Elderly High potentially mitigatable activity in England over the last 10 years. 

denominator_over_time<-tar_read(denominator_over_time)

plot_of_percentage_over_time(denominator_over_time, numbers_over_time, "frail_elderly_high", episodes, total_episodes_emergency)

```
#### Beddays
```{r, fig.width=8, fig.height=4}
#| label: fig-percent_trends_beddays_england
#| fig-cap: The percentage of total emergency beddays that are for Frail Elderly High potentially mitigatable activity in England over the last 10 years. 

plot_of_percentage_over_time(denominator_over_time, numbers_over_time, "frail_elderly_high", beddays, total_beddays_emergency)

```

:::


#### Standardised rate over time

::: panel-tabset

#### Admissions
```{r, fig.width=8, fig.height=4}



```

#### Beddays
:::


:::

### ICB

::: panel-tabset

#### Number over time
::: panel-tabset

#### Admissions
```{r, fig.width=8, fig.height=4}
#| label: fig-number_trends_spells_icb
#| fig-cap: The number of admissions for the Frail Elderly High mitigatable activity cohort by ICB over the last 9 years. 

icb_population_data<-tar_read(icb_population_data)

numbers_over_time|>
    filter(cohorts=="frail_elderly_high")|>
    filter(fyear!=201415)|>
    group_by( icb, year)|>
    summarise(activity=sum(episodes))|>
  left_join(tar_read(icb_population_data)[,c("icb24cdh", "icb_2024_name")], by=c("icb"="icb24cdh"))|>
 group_by(icb_2024_name)|>
  highlight_key(~icb_2024_name) |>
plot_ly( x = ~year, y = ~activity, type = 'scatter',  mode = 'lines', text=~icb_2024_name,  line = list(color = "#686f73",  width = 1.5))|>
  highlight(~icb_2024_name, on = "plotly_click", off="plotly_doubleclick", dynamic=TRUE)|>
   layout(
         xaxis = list(title=list(text='Year', font = list(size = 20), standoff = 25), showticklabels = TRUE, showline = TRUE, showgrid = F , linewidth=2),
         yaxis = list(title = 'Number', showline = TRUE, showgrid = F , linewidth=2 ,zeroline = FALSE, tickformat = "digits", anchor="free", shift=100)
         )


```
#### Beddays

```{r, fig.width=8, fig.height=4}
#| label: fig-number_trends_beddays_icb
#| fig-cap: The number of beddays for the Frail Elderly High mitigatable activity cohort by ICB over the last 9 years. 


```
:::

#### By proportion of emergency activity 
::: panel-tabset
#### Admissions
```{r, fig.width=8, fig.height=4}
#| label: fig-percent_trends_spells_icb
#| fig-cap: The percentage of total emergency admissions that are for Frail Elderly High potentially mitigatable activity by ICB over the last 9 years. 


```
#### Beddays
```{r, fig.width=8, fig.height=4}
#| label: fig-percent_trends_beddays_icb
#| fig-cap: The percentage of total emergency beddays that are for Frail Elderly High potentially mitigatable activity by ICB over the last 9 years. 


```

:::


#### Standardised rate over time

::: panel-tabset

#### Admissions


#### Beddays
:::

:::
## Comparative Analysis

### ICB

```{r}
#| output: false
data <- targets::tar_read(perc_spells_frail_icb) |>
  dplyr::mutate(icb = stringr::str_to_upper(icb))

icb_pop <- targets::tar_read(icb_population_data) |>
  dplyr::filter(fyear == "2023/24") |>
  dplyr::summarise(pop = sum(icb_population), .by = c(icb24cdh, icb_2024_code))

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names()

# notes
  # value = number spells at icb * 100 / population at icb
  # using 2023 icb shapefile
```

```{r}
#| label: fig-perc_frail_icb
#| fig-cap: Mitigable activity for Frail and Elderly Admissions in 2023-24 by icb.
icb_23_shp |>
  dplyr::left_join(icb_pop, by = c("icb23cd" = "icb_2024_code")) |>
  dplyr::left_join(data, by = c("icb24cdh" = "icb")) |>
  dplyr::mutate(value = janitor::round_half_up(spells * 100 /
                                                  pop, 2)) |>
  ggplot2::ggplot() +
  ggplot2::geom_sf(ggplot2::aes(fill = value)) +
  ggplot2::theme_void()
```

