# Redirection and Substitution

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")
source("R/manipulating_mitigators_and_mechanisms.R")

options(scipen = 999)
options(knitr.duplicate.label = "allow")
```

```{r global variables}
cohort <- "redirection_substitution"
cohort_title <- "Redirection and Substitution"
treatment_type <- "both"
treatment_type_title <- format_treatment_for_caption(treatment_type)
activity_type_label<-"admissions/beddays"
```

```{r}
#| output: false
mitigator_summary_table <- readxl::read_excel("summary_mitigators_table.xlsx") |>
  dplyr::mutate(mechanism = snakecase::to_snake_case(mechanism))

mechanisms <- mitigator_summary_table |> 
  dplyr::pull(mechanism) |> 
  unique()

england_age_sex_standardised_rates_episodes <- tar_read(england_age_sex_standardised_rates_episodes) |>
  filter(cohorts == cohort)

england_age_sex_standardised_rates_beddays <- tar_read(england_age_sex_standardised_rates_beddays) |>
  filter(cohorts == cohort)

total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names() |>
  dplyr::mutate(icb23nm = simplify_icb_name(icb23nm))
```

```{r including_activity_types}
include_admissions <- check_include_admissions(cohort, mitigator_summary_table)
include_beddays <- check_include_beddays(cohort)
include_admissions_and_beddays <- include_admissions & include_beddays
```

This analysis includes mitigators where the mechanism of action is through Redirection/Substitution of activity. This means that some of the admissions in this group could be avoided by greater use of other services/provisions in the community (either existing or new).

```{r}
#| output: asis
knitr::knit_child(
      input = "child-dir/_child-overview.qmd",
      envir = environment(),
      quiet = TRUE
    ) |>
      cat(sep = '\n')
```

## Descriptive Analysis of Mitigable Activity

### Patient Characteristics

::: panel-tabset
#### Age

```{r}
patient_characteristic <- "age"
patient_characteristic_col_name <- "age_range"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### Ethnicity

```{r}
patient_characteristic <- "ethnicity"
patient_characteristic_col_name <- "Ethnic_Category"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### IMD Decile

```{r}
patient_characteristic <- "imd"
patient_characteristic_col_name <- "imd19_decile"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### Sex

```{r}
patient_characteristic <- "sex"
patient_characteristic_col_name <- "sex"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```
:::

### Admission Characteristics

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_admission-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

## Cohort overlap

```{r}
overlap_numbers <- targets::tar_read(cohort_overlap_numbers_redirection)
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_number-within-others.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Most common cohort overlaps

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_most-common.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

## Comparative Analysis

### Integrated Care Board

```{r}
#| output: asis
knitr::knit_child(
                  input = "child-dir/_child-comparative_icb.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

### Local Authority

```{r}
#| output: asis
knitr::knit_child(
                  input = "child-dir/_child-comparative_local-authority.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

## Trend Analysis

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_england.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```


```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_icb.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Local Authority

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_local-authority.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```
