# Redirection and Substitution

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")

options(scipen = 999)
options(knitr.duplicate.label = "allow")
```

```{r global variables}
cohort <- "redirection_substitution"
cohort_title <- "Redirection and Substitution"
treatment_type <- "both"
treatment_type_title <- format_treatment_for_caption(treatment_type)
```

```{r}
#| output: false
mitigator_summary_table <- readxl::read_excel("summary_mitigators_table.xlsx") |>
  dplyr::mutate(mechanism = snakecase::to_snake_case(mechanism))

mechanisms <- mitigator_summary_table |> 
  dplyr::pull(mechanism) |> 
  unique()

england_age_sex_standardised_rates_episodes <- tar_read(england_age_sex_standardised_rates_episodes) |>
  filter(cohorts == cohort)

england_age_sex_standardised_rates_beddays <- tar_read(england_age_sex_standardised_rates_beddays) |>
  filter(cohorts == cohort)

total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names() |>
  dplyr::mutate(icb23nm = simplify_icb_name(icb23nm))
```

What this mechanism is...

## Descriptive Analysis of Mitigable Activity

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_overview.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Patient Characteristics

::: panel-tabset
#### Age
```{r}
patient_characteristic <- "age"
patient_characteristic_col_name <- "age_range"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristic.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### Ethnicity
```{r}
patient_characteristic <- "ethnicity"
patient_characteristic_col_name <- "Ethnic_Category"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristic.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### IMD
```{r}
patient_characteristic <- "imd"
patient_characteristic_col_name <- "imd19_decile"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristic.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### Sex
```{r}
patient_characteristic <- "sex"
patient_characteristic_col_name <- "sex"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristic.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```
:::

### Admission Characteristics

::: panel-tabset
### Length Of Stay

```{r}
perc_los_redirection_substitution <- targets::tar_read(perc_los_redirection_substitution)
```

```{r}
#| label: tbl-perc_los_redirection_substitution
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "los", treatment_type)
perc_los_redirection_substitution |>
  get_perc_by_los_table()
```

```{r}
#| label: fig-perc_los_redirection_substitution
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "los", treatment_type)
perc_los_redirection_substitution |>
  get_perc_by_los_plot()
```

### Specialty

::: panel-tabset
#### Admissions

```{r}
#| label: tbl-perc_specialty_redirection_substitution_admissions
#| tbl-cap: !expr get_caption_top_ten_specialties(cohort_title, "admissions")
targets::tar_read(specialty_redirection_substitution_admissions) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_specialty_redirection_substitution_admissions
#| fig-cap: !expr get_caption_top_ten_specialties(cohort_title, "admissions")
targets::tar_read(specialty_redirection_substitution_admissions)  |>
  get_top_ten_specialties_plot("admissions")
```

#### Beddays

```{r}
#| label: tbl-perc_specialty_redirection_substitution_beddays
#| tbl-cap: !expr get_caption_top_ten_specialties(cohort_title, "beddays")
targets::tar_read(specialty_redirection_substitution_beddays) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_specialty_redirection_substitution_beddays
#| fig-cap: !expr get_caption_top_ten_specialties(cohort_title, "beddays")
targets::tar_read(specialty_redirection_substitution_beddays) |>
  get_top_ten_specialties_plot("beddays")
```
:::
:::

## Cohort overlap

Many admissions meet the criteria to be included in more than one mitigator cohort. Since these potential mitigator cohorts are not mutually exclusive there is a need to understand which cohorts overlap and the degree of overlap between the cohorts.

### Number and proportion within multiple other cohorts

For the Redirection/Substitution mechanism group we show how much of the activity is included in other Redirection/Substitution groups. 

```{r}
overlap_numbers <- targets::tar_read(cohort_overlap_numbers_redirection)
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_number-within-others.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Most common cohort overlaps

Often overlap between a small number of groups can be visualised using Venn diagram. However, due to the large number of mitigator cohorts and therefore high numbers of potential combinations of overlaps we have used upset plots to show the largest overlaps between cohorts.

The 15 most common cohort combinations for the Redirection/Substitution mechanism group are shown. 

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_most-common.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

## Comparative Analysis

::: panel-tabset
### Admissions

```{r}
#| output: asis
activity_type <- "admissions"
standardised_rates <- england_age_sex_standardised_rates_episodes

knitr::knit_child(
                  input = "child-dir/_child-comparative.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

### Beddays

```{r}
#| output: asis
activity_type <- "beddays"
standardised_rates <- england_age_sex_standardised_rates_beddays

knitr::knit_child(
                  input = "child-dir/_child-comparative.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

:::

## Trend Analysis

We aim to understand whether there have been decreases, or increases, in potentially mitigable Redirection and Substitution activity over time. We have considered Redirection and Substitution admissions and beddays over the past 9 years in England as a whole and for each ICB, including:

a\) the absolute number of Redirection and Substitution admissions/beddays,

b\) these admissions/beddays as a proportion of emergency admissions,

c\) the age and sex standardised rates of these admissions/beddays using the England 2021 census population.

To help understand the variability between ICBs we have calculated for each ICB the percentage change in proportion of emergency admissions and in standardised rates between 2018/19 and 2023/24.

### England

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_england.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### ICB

Note: Low numbers of admissions/beddays for Frimley ICB in 2022/23 reflect an issue with data submissions for this period. 

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_icb.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Local Authority

Age and sex standardised rates of activity for local authority areas. 

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_local-authority.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```
