# Redirection and Substitution

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")

options(scipen = 999)
```

```{r global variables}
cohort <- "redirection_substitution"
cohort_title <- "Redirection and Substitution"
treatment_type <- "both"
```

```{r}
# england_age_sex_standardised_rates_episodes<-tar_read(england_age_sex_standardised_rates_episodes)|>
#   filter(cohorts==cohort)
# 
# england_age_sex_standardised_rates_beddays<-tar_read(england_age_sex_standardised_rates_beddays)|>
#   filter(cohorts==cohort)
```

What this mechanism is...

## Descriptive Analysis of Mitigable Activity

```{r}
overview_redirection_substitution <- targets::tar_read(overview_redirection_substitution)

redirection_substitution_admissions_perc <- overview_redirection_substitution |>
  dplyr::filter(activity_type == "Admissions") |>
  dplyr::pull(perc)

redirection_substitution_beddays_perc <- overview_redirection_substitution |>
  dplyr::filter(activity_type == "Beddays") |>
  dplyr::pull(perc)
```

In 2023/24, `r redirection_substitution_admissions_perc`% of all emergency admissions and `r redirection_substitution_beddays_perc`% of all emergency beddays fall under mitigable activity for the Frail Older People (high frailty) cohort (@tbl-perc_redirection_substitution).

```{r}
#| label: tbl-perc_redirection_substitution
#| tbl-cap: !expr get_caption_overview(cohort_title, treatment_type)
overview_redirection_substitution |>
  get_table_perc()
```

...

