# Methodology {#sec-methods .unnumbered}

```{r}
library(flextable)
```

## Hospital activity data

All data on hospital activity are taken from the New Hospitals Programme (NHP) demand and capacity model data, which is derived from the [Hospital Episode Statistics dataset](https://digital.nhs.uk/services/hospital-episode-statistics). 

The potentially mitigable activity for the 29 mitigator cohorts of interest is taken from the dataset used for the NHP Demand and Capacity Model. All activity that meets the criteria for potentially mitigable is included, but it should be noted that in practice only a proportion of this activity would be truly mitigable. The code used to define the potentially mitigable activity can be found here- <https://github.com/The-Strategy-Unit/nhp_data/tree/main/raw_data/mitigators/ip>

Where data is given for Integrated Care Boards (ICBs) these are based on the 2024 ICBs. The ICB is determined based on the patient being resident within the ICB area, in records where the resident ICB field is empty the responsible ICB is used instead.

Where data is given for  Local Authorities (LAs) these are the 2023 LAs; LA data is missing in approximately 1% of records. The local authority is the local authority district of residence of the patient derived from the patient’s postcode. 

Where Index of Multiple Deprivation (IMD) deciles are shown these are the 2019 values.  

Admissions are calculated, as per the NHP model, by using the last episode in a spell. So, where a spell consists of more than one episode only the last is counted. If a person has more than one admission they will be counted multiple times within the dataset.

The beddays for an admission are calculated based from the number of days between admission date and discharge date, so if a person was admitted and discharged on the same day the beddays for the admission would be counted as zero.

For 4 mitigators (Alcohol related admissions (Acute conditions- partially attributable), Alcohol related admissions (Chronic conditions- partially attributable), Obesity related admissions and Smoking related admissions) it is considered that only a proportion of the activity included in these groups can be attributed to alcohol/obesity/smoking. For example, certain cancers/cardiovascular disease are included within this group, but only a proportion of those will be due to alcohol/obesity/smoking. Therefore, activity for these mitigators has been adjusted using the attributable fractions found here-  <https://github.com/The-Strategy-Unit/nhp_data/tree/main/raw_data/mitigators/reference_data>.
Due to using the attributable fractions to the adjustment the activity within the mitigator groups there are possibly very slight discrepancies in the numbers within the report as a result of rounding the admissions and beddays to be whole numbers. 

## Population data 

ICB populations for each year are from the Office of National Statistics mid year population estimates -  <https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/datasets/clinicalcommissioninggroupmidyearpopulationestimates>. As 2023/24 ICB population data was not available the 2022/23 data was also used for 2023/24.

Local authority populations for each year are from the Office of National Statistics Estimates of the population for England and Wales dataset -  <https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/datasets/estimatesofthepopulationforenglandandwales>

The age and sex standardised rates are calculated using population data for England from the 2021 census as the standard population - <https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/bulletins/populationandhouseholdestimatesenglandandwales/census2021>. In a small number of cases where age or sex is not recorded the data has been excluded from the standardised rates.

For crude rates by IMD decile, the Office of National Statistics Lower layer Super Output Area population estimates for 2022 <https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/datasets/lowersuperoutputareamidyearpopulationestimates> were used and linked with the LSOA English indices of deprivation 2019
<https://www.gov.uk/government/statistics/english-indices-of-deprivation-2019>. Using the LSOA11 to LSOA21 look-up  <https://geoportal.statistics.gov.uk/search?sort=Date%20Created%7Ccreated%7Cdesc&tags=LUP_EXACT_LSOA11_LSOA21>.

For crude rates by ethnicity the Office of National Statistics Ethnic group, England and Wales: Census 2021 dataset was used - <https://www.ons.gov.uk/peoplepopulationandcommunity/culturalidentity/ethnicity/bulletins/ethnicgroupenglandandwales/census2021>. Data was recoded into [NHS ethnic categories](https://digital.nhs.uk/data-and-information/data-collections-and-data-sets/data-sets/mental-health-services-data-set/submit-data/data-quality-of-protected-characteristics-and-other-vulnerable-groups/ethnicity#how-to-collect-and-record-ethnicity-data). NULL and unknown values were excluded.

## Providers

```{r}
providers_2324_acute <- targets::tar_read(provider_type) |>
  dplyr::filter(year == "2023/24" & org_type == "Acute")
```


In 2023/24, acute NHS providers account for `r providers_2324_acute |> dplyr::pull(perc_admissions)`% of potentially mitigable admissions and `r providers_2324_acute |> dplyr::pull(perc_beddays)`% of potentially mitigable beddays. Similar numbers were observed for years 2018/19 to 2022/23. Thus, analyses of potentially mitigable activity by provider are for acute NHS providers only.

```{r}
#| label: tbl-provider_type
#| tbl-cap: Potentially mitigable activity by provider type in 2023/24.
targets::tar_read(provider_type_2324_table)
```

## Analysis

The analysis uses the most recent year of data available, 2023/24, except for trends analysis where analysis includes data from the last 9 years.

The majority of the mitigators are for activity avoidance, therefore these mitigators will impact the number of admissions, and through changes in admissions will also influence the number of beddays. However, 3 mitigators (Emergency Admission of Older People, Stroke Early Supported Discharge and Admissions with Mental Health Comorbidities) are efficiency mitigators, meaning that the admissions can't be avoided but the length of stay could be reduced by impacting the number of beddays. For these 3 mitigators we therefore only consider the number of beddays and not the number of admissions.

Where the activity for the cohort is given as a percentage of total activity, the percentage of admissions for each cohort are calculated relative to the total number of emergency admissions or total number of elective and emergency admissions depending on whether the mitigator cohort is defined as being only emergency admissions or can be either elective or emergency admissions.

### Comparative analysis

Maps of ICBS areas are plotted using the 2023 ICB shapefile, but 2024 ICB codes/names are used.
ICB shapefile: <https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson>

Maps of Local Authority areas are plotted using the 2024 LA shapefile, but 2023 LA names/codes are used.
LA shapefile: <https://geoportal.statistics.gov.uk/datasets/6a05f93297cf4a438d08e972099f54b9_0/explore>

### Trend analysis

The mitigable activity is given as a proportion of either total emergency activity or total emergency and elective activity for the whole population, dependent on whether the mitigable activity is defined as only emergency activity or can be either emergency or elective.

The age and sex standardised rates are the rate of admissions/beddays for the whole population of England, standardised to the England population from the 2021 census. 

Where percentage changes over time are calculated, the changes are calculated for the most recent 5 years, 2018/19 to 2023/25. 

## Limitations

We are using routinely reported data and therefore there may be issues with data recording/submissions or just discrepancies with how activity is recorded in different providers, which may impact the results. There may also have been changes in how activity is recorded in different areas over time.

The mitigator cohorts used are fairly broadly defined and we do not expect all activity within a cohort to be mitigable; it is likely that only a small proportion of the activity in each mitigator cohort will be truely mitigable.

With this type of analysis there is a risk of post hoc rationalisation; many admissions may be necessary at the time due to a potential clinical risk but afterwards may appear to have been potentially avoidable.  
