# Frail Older People (High Frailty Risk) Cohort {#sec-frail-elderly-high .unnumbered}

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")
library("DT")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")

options(scipen = 999)
options(knitr.duplicate.label = "allow")
```

```{r global variables}
cohort <- "frail_elderly_high"
cohort_title <- "Frail Older People (high frailty)"
treatment_type <- "emergency"
treatment_type_title <- format_treatment_for_caption(treatment_type)
```

```{r}
#| output: false
mitigator_summary_table <- readxl::read_excel("summary_mitigators_table.xlsx") |>
  dplyr::mutate(mechanism = snakecase::to_snake_case(mechanism))

mechanisms <- mitigator_summary_table |> 
  dplyr::pull(mechanism) |> 
  unique()

england_age_sex_standardised_rates_episodes <- tar_read(england_age_sex_standardised_rates_episodes) |>
  filter(cohorts == cohort)

england_age_sex_standardised_rates_beddays <- tar_read(england_age_sex_standardised_rates_beddays) |>
  filter(cohorts == cohort)

total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names() |>
  dplyr::mutate(icb23nm = simplify_icb_name(icb23nm))
```

This cohort includes older patients with a high level of frailty, specifically, those 75 years of age or over with an emergency admission and a frailty score over 15. The frailty score is calculated from ICD-10 diagnoses recorded for admissions during the previous 2 years and using the risk scores in Gilbert et al (2018), Development and validation of a Hospital Frailty Risk Score focusing on older people in acute care settings using electronic hospital records: an observational study. The Lancet, 391(10132), pp.1775-1782.

## Descriptive Analysis of Mitigable Activity

```{r}
overview <- targets::tar_read(overview_frail_elderly_high)

frail_elderly_high_admissions_perc <- overview |>
  dplyr::filter(activity_type == "Admissions") |>
  dplyr::pull(perc)

frail_elderly_high_beddays_perc <- overview |>
  dplyr::filter(activity_type == "Beddays") |>
  dplyr::pull(perc)
```

In 2023/24, `r frail_elderly_high_admissions_perc`% of all emergency admissions and `r frail_elderly_high_beddays_perc`% of all emergency beddays fall under mitigable activity for the Frail Older People (high frailty) cohort (@tbl-perc_frail_elderly_high).

```{r}
#| label: tbl-perc_frail_elderly_high
#| tbl-cap: !expr get_caption_overview(cohort_title, treatment_type)
overview |>
  get_table_perc()
```

### Patient Characteristics

In this section, the number and percentage of mitigable activity for the Frail Older People (high frailty) cohort are shown by patient characteristics: age, ethnic category, IMD decile and sex. Crude rates per 100,000 population are also provided for context.

Outputs are presented for both admissions and beddays, but patterns are broadly similar across the two.

::: panel-tabset
### Admissions

::: panel-tabset
### Age

```{r}
perc_age_frail_elderly_high_admissions <- targets::tar_read(perc_age_frail_elderly_high_admissions)
rates_age_frail_elderly_high_admissions <- targets::tar_read(rates_age_frail_elderly_high_admissions)
```

Of 2023/24 mitigable admissions for the Frail Older People (high frailty) cohort, most patients (`r perc_age_frail_elderly_high_admissions |> dplyr::filter(age_range == "85-89") |> dplyr::pull(perc)`%) are in the 85-89 year old age group (@tbl-perc_age_frail_elderly_high_admissions). Although the percentages for each age group are roughly similar, the rates of mitigable admissions per 100,000 population increases with age, with the 90+ age group having the highest rates at `r rates_age_frail_elderly_high_admissions |> dplyr::filter(age_range == "90+") |> dplyr::pull(value) |> prettyNum(big.mark = ",")` per 100,000 (@tbl-rate_frail_elderly_high_age_admissions).

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_age_frail_elderly_high_admissions
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "age group", treatment_type)
perc_age_frail_elderly_high_admissions |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_age_frail_elderly_high_admissions
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "age group", treatment_type)
perc_age_frail_elderly_high_admissions |>
  get_perc_by_group_plot("age_range", "admissions")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_age_admissions
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "age group")
rates_age_frail_elderly_high_admissions |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_age_admissions
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "age group")
rates_age_frail_elderly_high_admissions |>
  get_rates_by_group_plot("age_range")
```
:::

### Ethnicity

```{r}
perc_ethnicity_frail_elderly_high_admissions <- targets::tar_read(perc_ethnicity_frail_elderly_high_admissions)
rates_ethnicity_frail_elderly_high_admissions <- targets::tar_read(rates_ethnicity_frail_elderly_high_admissions)
```

Patients in the White ethnic group make up the majority (`r perc_ethnicity_frail_elderly_high_admissions |> dplyr::filter(Ethnic_Category == "White") |> dplyr::pull(perc)`%) of 2023-24 mitigable admissions for the Frail Older People (high frailty) cohort and have the highest rates (`r rates_ethnicity_frail_elderly_high_admissions |> dplyr::filter(Ethnic_Category == "White") |> dplyr::pull(value) |> prettyNum(big.mark = ",")`) per 100,000 population.

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_ethnicity_frail_elderly_high_admissions
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "ethnicity", treatment_type)
perc_ethnicity_frail_elderly_high_admissions |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_ethnicity_frail_elderly_high_admissions
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "ethnicity", treatment_type)
perc_ethnicity_frail_elderly_high_admissions |>
  get_perc_by_group_plot("Ethnic_Category", "admissions")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_ethnicity_admissions
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "ethnicity")
rates_ethnicity_frail_elderly_high_admissions |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_ethnicity_admissions
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "ethnicity")
rates_ethnicity_frail_elderly_high_admissions |>
  get_rates_by_group_plot("Ethnic_Category")
```
:::

### IMD

```{r}
perc_imd_frail_elderly_high_admissions <- targets::tar_read(perc_imd_frail_elderly_high_admissions)
rates_imd_frail_elderly_high_admissions <- targets::tar_read(rates_imd_frail_elderly_high_admissions)
```

The percentage of 2023/24 mitigable admissions for the Frail Older People (high frailty) cohort appear similar across the IMD deciles. Patients from areas with IMD deciles 7-9 have the highest rates of mitigable admission per 100,000 (@tbl-rate_frail_elderly_high_imd_admissions). However, there is little difference between patients from the most deprived areas (decile 1) compared to those from the least deprived areas (decile 10).

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_imd_frail_elderly_high_admissions
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "imd", treatment_type)
perc_imd_frail_elderly_high_admissions |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_imd_frail_elderly_high_admissions
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "imd", treatment_type)
perc_imd_frail_elderly_high_admissions |>
  get_perc_by_group_plot("imd19_decile", "admissions")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_imd_admissions
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "imd")
rates_imd_frail_elderly_high_admissions |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_imd_admissions
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "imd")
rates_imd_frail_elderly_high_admissions |>
  get_rates_by_group_plot("imd19_decile")
```
:::

### Sex

```{r}
perc_sex_frail_elderly_high_admissions <- targets::tar_read(perc_sex_frail_elderly_high_admissions)
rates_sex_frail_elderly_high_admissions <- targets::tar_read(rates_sex_frail_elderly_high_admissions)
```

The majority (`r perc_sex_frail_elderly_high_admissions |> dplyr::filter(sex == "Female") |> dplyr::pull(perc)`%) of mitigable admissions for the Frail Older People (high frailty) cohort are for female patients. Females also have the higher rate per 100,000 at `r rates_sex_frail_elderly_high_admissions |> dplyr::filter(sex == "Female") |> dplyr::pull(value) |> prettyNum(big.mark = ",")` compared to `r rates_sex_frail_elderly_high_admissions |> dplyr::filter(sex == "Male") |> dplyr::pull(value) |> prettyNum(big.mark = ",")` for males (@tbl-rate_frail_elderly_high_sex_admissions).

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_sex_frail_elderly_high_admissions
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "sex", treatment_type)
perc_sex_frail_elderly_high_admissions |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_sex_frail_elderly_high_admissions
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "sex", treatment_type)
perc_sex_frail_elderly_high_admissions |>
  get_perc_by_group_plot("sex", "admissions")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_sex_admissions
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "sex")
rates_sex_frail_elderly_high_admissions |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_sex_admissions
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "admissions", "sex")
rates_sex_frail_elderly_high_admissions |>
  get_rates_by_group_plot("sex")
```
:::
:::

### Beddays

::: panel-tabset
### Age

```{r}
perc_age_frail_elderly_high_beddays <- targets::tar_read(perc_age_frail_elderly_high_beddays)
rates_age_frail_elderly_high_beddays <- targets::tar_read(rates_age_frail_elderly_high_beddays)
```

Of 2023/24 mitigable beddays for the Frail Older People (high frailty) cohort, most patients (`r perc_age_frail_elderly_high_beddays |> dplyr::filter(age_range == "85-89") |> dplyr::pull(perc)`%) are in the 85-89 year old age group (@tbl-perc_age_frail_elderly_high_beddays). Although the percentages for each age group are roughly similar, the rates of mitigable beddays per 100,000 population increases with age, with the 90+ age group having the highest rates at `r rates_age_frail_elderly_high_beddays |> dplyr::filter(age_range == "90+") |> dplyr::pull(value) |> prettyNum(big.mark = ",")` per 100,000 (@tbl-rate_frail_elderly_high_age_beddays).

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_age_frail_elderly_high_beddays
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "age group", treatment_type)
targets::tar_read(perc_age_frail_elderly_high_beddays) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_age_frail_elderly_high_beddays
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "age group", treatment_type)
targets::tar_read(perc_age_frail_elderly_high_beddays) |>
  get_perc_by_group_plot("age_range", "beddays")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_age_beddays
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "age group")
targets::tar_read(rates_age_frail_elderly_high_beddays) |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_age_beddays
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "age group")
targets::tar_read(rates_age_frail_elderly_high_beddays) |>
  get_rates_by_group_plot("age_range")
```
:::

### Ethnicity

```{r}
perc_ethnicity_frail_elderly_high_beddays <- targets::tar_read(perc_ethnicity_frail_elderly_high_beddays)
rates_ethnicity_frail_elderly_high_beddays <- targets::tar_read(rates_ethnicity_frail_elderly_high_beddays)
```

Patients in the White ethnic group make up the majority (`r perc_ethnicity_frail_elderly_high_beddays |> dplyr::filter(Ethnic_Category == "White") |> dplyr::pull(perc)`%) of 2023-24 mitigable beddays for the Frail Older People (high frailty) cohort and have the highest rates (`r rates_ethnicity_frail_elderly_high_beddays |> dplyr::filter(Ethnic_Category == "White") |> dplyr::pull(value) |> prettyNum(big.mark = ",")`) per 100,000 population.

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_ethnicity_frail_elderly_high_beddays
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "ethnicity", treatment_type)
targets::tar_read(perc_ethnicity_frail_elderly_high_beddays) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_ethnicity_frail_elderly_high_beddays
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "ethnicity", treatment_type)
targets::tar_read(perc_ethnicity_frail_elderly_high_beddays) |>
  get_perc_by_group_plot("Ethnic_Category", "beddays")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_ethnicity_beddays
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "ethnicity")
targets::tar_read(rates_ethnicity_frail_elderly_high_beddays) |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_ethnicity_beddays
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "ethnicity")
targets::tar_read(rates_ethnicity_frail_elderly_high_beddays) |>
  get_rates_by_group_plot("Ethnic_Category")
```
:::

### IMD

```{r}
perc_imd_frail_elderly_high_beddays <- targets::tar_read(perc_imd_frail_elderly_high_beddays)
rates_imd_frail_elderly_high_beddays <- targets::tar_read(rates_imd_frail_elderly_high_beddays)
```

The percentage of 2023/24 mitigable beddays for the Frail Older People (high frailty) cohort appear similar across the IMD deciles. Patients from areas with IMD deciles 7-9 have the highest rates of mitigable admission per 100,000 @tbl-rate_frail_elderly_high_imd_beddays. However, there is little difference between patients from the most deprived areas (decile 1) compared to those from the least deprived areas (decile 10).

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_imd_frail_elderly_high_beddays
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "imd", treatment_type)
targets::tar_read(perc_imd_frail_elderly_high_beddays) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_imd_frail_elderly_high_beddays
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "imd", treatment_type)
targets::tar_read(perc_imd_frail_elderly_high_beddays) |>
  get_perc_by_group_plot("imd19_decile", "beddays")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_imd_beddays
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "imd")
targets::tar_read(rates_imd_frail_elderly_high_beddays) |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_imd_beddays
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "imd")
targets::tar_read(rates_imd_frail_elderly_high_beddays) |>
  get_rates_by_group_plot("imd19_decile")
```
:::

### Sex

```{r}
perc_sex_frail_elderly_high_beddays <- targets::tar_read(perc_sex_frail_elderly_high_beddays)
rates_sex_frail_elderly_high_beddays <- targets::tar_read(rates_sex_frail_elderly_high_beddays)
```

The majority (`r perc_sex_frail_elderly_high_beddays |> dplyr::filter(sex == "Female") |> dplyr::pull(perc)`%) of mitigable beddays for the Frail Older People (high frailty) cohort are for female patients. Females also have the higher rate per 100,000 at `r rates_sex_frail_elderly_high_beddays |> dplyr::filter(sex == "Female") |> dplyr::pull(value) |> prettyNum(big.mark = ",")` compared to `r rates_sex_frail_elderly_high_beddays |> dplyr::filter(sex == "Male") |> dplyr::pull(value) |> prettyNum(big.mark = ",")` for males (@tbl-rate_frail_elderly_high_sex_beddays).

::: panel-tabset
#### Percentage of `r treatment_type_title` activity

```{r}
#| label: tbl-perc_sex_frail_elderly_high_beddays
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "sex", treatment_type)
targets::tar_read(perc_sex_frail_elderly_high_beddays) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_sex_frail_elderly_high_beddays
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "beddays", "sex", treatment_type)
targets::tar_read(perc_sex_frail_elderly_high_beddays) |>
  get_perc_by_group_plot("sex", "beddays")
```

#### Crude rate

```{r}
#| label: tbl-rate_frail_elderly_high_sex_beddays
#| tbl-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "sex")
targets::tar_read(rates_sex_frail_elderly_high_beddays) |>
  get_rates_by_group_table() 
```

```{r}
#| label: fig-rate_frail_elderly_high_sex_beddays
#| fig-cap: !expr get_caption_by_group("rate", cohort_title, "beddays", "sex")
targets::tar_read(rates_sex_frail_elderly_high_beddays) |>
  get_rates_by_group_plot("sex")
```
:::
:::
:::

### Admission Characteristics

In this section, mitigable activity for the Frail Older People (high frailty) cohort are shown by admission characteristics.

::: panel-tabset
### Length Of Stay

```{r}
perc_los_frail_elderly_high <- targets::tar_read(perc_los_frail_elderly_high)
```

Of the 2023/24 mitigable admissions for Frail Older People (high frailty) cohort, most (`r perc_los_frail_elderly_high |> dplyr::filter(weeks == 1) |> dplyr::pull(perc_weeks) |> purrr::pluck(1)`%) length of stays are under 1 week and `r perc_los_frail_elderly_high |> dplyr::filter(los_range == 0) |> dplyr::pull(perc)`% are less than 1 day.

```{r}
#| label: tbl-perc_los_frail_elderly_high
#| tbl-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "los", treatment_type)
perc_los_frail_elderly_high |>
  get_perc_by_los_table()
```

```{r}
#| label: fig-perc_los_frail_elderly_high
#| fig-cap: !expr get_caption_by_group("perc", cohort_title, "admissions", "los", treatment_type)
perc_los_frail_elderly_high |>
  get_perc_by_los_plot()
```

### Specialty

Across both admissions and beddays, the largest two treatment functions for mitigable activity for the Frail Older People (high frailty) cohort are Elderly Medicine Service and General Internal Medicine Service.

::: panel-tabset
#### Admissions

```{r}
#| label: tbl-perc_specialty_frail_elderly_high_admissions
#| tbl-cap: !expr get_caption_top_ten_specialties(cohort_title, "admissions")
targets::tar_read(specialty_frail_elderly_high_admissions) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_specialty_frail_elderly_high_admissions
#| fig-cap: !expr get_caption_top_ten_specialties(cohort_title, "admissions")
targets::tar_read(specialty_frail_elderly_high_admissions)  |>
  get_top_ten_specialties_plot("admissions")
```

#### Beddays

```{r}
#| label: tbl-perc_specialty_frail_elderly_high_beddays
#| tbl-cap: !expr get_caption_top_ten_specialties(cohort_title, "beddays")
targets::tar_read(specialty_frail_elderly_high_beddays) |>
  get_table_perc() 
```

```{r}
#| label: fig-perc_specialty_frail_elderly_high_beddays
#| fig-cap: !expr get_caption_top_ten_specialties(cohort_title, "beddays")
targets::tar_read(specialty_frail_elderly_high_beddays) |>
  get_top_ten_specialties_plot("beddays")
```
:::
:::

## Cohort overlap

Many admissions meet the criteria to be included in more than one mitigator cohort. Since these potential mitigator cohorts are not mutually exclusive there is a need to understand which cohorts overlap and the degree of overlap between the cohorts.

### Number and proportion within multiple other cohorts

For the Frail Older People (high frailty) activity we show how much of the activity is included in multiple other mitigable cohorts. There are some differences between cohort overlap for admissions and beddays, this is because efficiency mitigators are not included in admissions data as they do not impact the number of admissions, but are included in the beddays data as they influence length of stay. 

```{r}
overlap_numbers <- targets::tar_read(total_cohort_numbers_2324)|>
  filter(!!rlang::sym(cohort) == 1)
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_number-within-others.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Inclusion within other mitigable activity cohorts

This shows whether the activity within the Elderly Frail High activity is also included in other mitigator cohorts, including where this occurs the number and percentage of Elderly Frail High activity that is also included within other mitigator cohorts.

For example, Elderly Frail High cohort overlaps with all but 2 of the other mitigator cohorts. All the Elderly Frail High cohort activity is also included in the Emergency Elderly cohort, and 63% of this cohort are in the Alcohol Partially Attributable Chronic cohort.

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_inclusion-within-others.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Most common cohort overlaps

Often overlap between a small number of groups can be visualised using Venn diagram. However, due to the large number of mitigator cohorts and therefore high numbers of potential combinations of overlaps we have used upset plots to show the largest overlaps between cohorts.

The 15 most common cohort combinations for the Elderly Frail High cohort are shown. For this cohort there are a very large number of different cohort combinations, so there are many smaller size cohort combinations that are not shown (all combinations together would add to 100%).

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_most-common.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

## Comparative Analysis

::: panel-tabset
### Admissions

```{r}
#| output: asis
activity_type <- "admissions"
standardised_rates <- england_age_sex_standardised_rates_episodes

knitr::knit_child(
                  input = "child-dir/_child-comparative.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

### Beddays

```{r}
#| output: asis
activity_type <- "beddays"
standardised_rates <- england_age_sex_standardised_rates_beddays

knitr::knit_child(
  input = "child-dir/_child-comparative.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

:::

## Trend Analysis

We aim to understand whether there have been decreases, or increases, in potentially mitigable Frail Older People (high frailty) activity over time. We have considered Frail Older People (high frailty) admissions and beddays over the past 9 years in England as a whole and for each ICB, including:

a\) the absolute number of Frail Older People (high frailty) admissions/beddays,

b\) these admissions/beddays as a proportion of emergency admissions,

c\) the age and sex standardised rates of these admissions/beddays using the England 2021 census population.

To help understand the variability between ICBs we have calculated for each ICB the percentage change in proportion of emergency admissions and in standardised rates between 2018/19 and 2023/24.

### England

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_england.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### ICB

Note: Low numbers of admissions/beddays for Frimley ICB in 2022/23 reflect an issue with data submissions for this period. 

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_icb.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Local Authority

Age and sex standardised rates of activity for local authority areas 

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_local-authority.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```
