# Frail Older People (High Frailty Risk) Cohort {#sec-frail-elderly-high .unnumbered}

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")
library("DT")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")
source("R/manipulating_mitigators_and_mechanisms.R")

options(scipen = 999)
options(knitr.duplicate.label = "allow")
```

```{r global variables}
cohort <- "frail_elderly_high"
cohort_title <- "Frail Older People (high frailty)"
treatment_type <- "emergency"
treatment_type_title <- format_treatment_for_caption(treatment_type)
```

```{r}
#| output: false
mitigator_summary_table <- readxl::read_excel("summary_mitigators_table.xlsx") |>
  dplyr::mutate(mechanism = snakecase::to_snake_case(mechanism))

mechanisms <- mitigator_summary_table |> 
  dplyr::pull(mechanism) |> 
  unique()

england_age_sex_standardised_rates_episodes <- tar_read(england_age_sex_standardised_rates_episodes) |>
  filter(cohorts == cohort)

england_age_sex_standardised_rates_beddays <- tar_read(england_age_sex_standardised_rates_beddays) |>
  filter(cohorts == cohort)

total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names() |>
  dplyr::mutate(icb23nm = simplify_icb_name(icb23nm))
```

```{r including_activity_types}
include_admissions <- check_include_admissions(cohort, mitigator_summary_table)
include_beddays <- check_include_beddays(cohort)
include_admissions_and_beddays <- include_admissions & include_beddays
```

This cohort includes older patients with a high level of frailty, specifically, those 75 years of age or over with an emergency admission and a frailty score over 15. The frailty score is calculated from ICD-10 diagnoses recorded for admissions during the previous 2 years and using the risk scores in Gilbert et al (2018), Development and validation of a Hospital Frailty Risk Score focusing on older people in acute care settings using electronic hospital records: an observational study. The Lancet, 391(10132), pp.1775-1782.

## Descriptive Analysis of Mitigable Activity

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_overview.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Patient Characteristics

In this section, the number and percentage of mitigable activity for the Frail Older People (high frailty) cohort are shown by patient characteristics: age, ethnic category, IMD decile and sex. Crude rates per 100,000 population are also provided for context.

Outputs are presented for both admissions and beddays, but patterns are broadly similar across the two.

::: panel-tabset
#### Age
```{r}
patient_characteristic <- "age"
patient_characteristic_col_name <- "age_range"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### Ethnicity
```{r}
patient_characteristic <- "ethnicity"
patient_characteristic_col_name <- "Ethnic_Category"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### IMD Decile
```{r}
patient_characteristic <- "imd"
patient_characteristic_col_name <- "imd19_decile"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

#### Sex
```{r}
patient_characteristic <- "sex"
patient_characteristic_col_name <- "sex"
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_patient-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```
:::

### Admission Characteristics

In this section, mitigable activity for the Frail Older People (high frailty) cohort are shown by admission characteristics.

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-descriptive_admission-characteristics.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

## Cohort overlap

Many admissions meet the criteria to be included in more than one mitigator cohort. Since these potential mitigator cohorts are not mutually exclusive there is a need to understand which cohorts overlap and the degree of overlap between the cohorts.

### Number and proportion within multiple other cohorts

For the Frail Older People (high frailty) activity we show how much of the activity is included in multiple other mitigable cohorts. There are some differences between cohort overlap for admissions and beddays, this is because efficiency mitigators are not included in admissions data as they do not impact the number of admissions, but are included in the beddays data as they influence length of stay. 

```{r}
overlap_numbers <- targets::tar_read(total_cohort_numbers_2324)|>
  filter(!!rlang::sym(cohort) == 1)
```

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_number-within-others.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Inclusion within other mitigable activity cohorts

This shows whether the activity within the Elderly Frail High activity is also included in other mitigator cohorts, including where this occurs the number and percentage of Elderly Frail High activity that is also included within other mitigator cohorts.

For example, Elderly Frail High cohort overlaps with all but 2 of the other mitigator cohorts. All the Elderly Frail High cohort activity is also included in the Emergency Elderly cohort, and 63% of this cohort are in the Alcohol Partially Attributable Chronic cohort.

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_inclusion-within-others.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Most common cohort overlaps

Often overlap between a small number of groups can be visualised using Venn diagram. However, due to the large number of mitigator cohorts and therefore high numbers of potential combinations of overlaps we have used upset plots to show the largest overlaps between cohorts.

The 15 most common cohort combinations for the Elderly Frail High cohort are shown. For this cohort there are a very large number of different cohort combinations, so there are many smaller size cohort combinations that are not shown (all combinations together would add to 100%).

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-overlap_most-common.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

## Comparative Analysis

### Integrated Care Board

```{r}
#| output: asis
knitr::knit_child(
                  input = "child-dir/_child-comparative_icb.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

### Local Authority

```{r}
#| output: asis
knitr::knit_child(
                  input = "child-dir/_child-comparative_local-authority.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

## Trend Analysis

We aim to understand whether there have been decreases, or increases, in potentially mitigable Frail Older People (high frailty) activity over time. We have considered Frail Older People (high frailty) admissions and beddays over the past 9 years in England as a whole and for each ICB, including:

a\) the absolute number of Frail Older People (high frailty) admissions/beddays,

b\) these admissions/beddays as a proportion of `r treatment_type_title` admissions,

c\) the age and sex standardised rates of these admissions/beddays using the England 2021 census population.

To help understand the variability between ICBs we have calculated for each ICB the percentage change in proportion of emergency admissions and in standardised rates between 2018/19 and 2023/24.

### England

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_england.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')

```

### Integrated Care Board

Note: Low numbers of admissions/beddays for Frimley ICB in 2022/23 reflect an issue with data submissions for this period. 

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_icb.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```

### Local Authority

Age and sex standardised rates of activity per 100,000 population for local authority areas. 

```{r}
#| output: asis
knitr::knit_child(
  input = "child-dir/_child-trends_local-authority.qmd",
  envir = environment(),
  quiet = TRUE
  ) |>
  cat(sep = '\n')
```
