# Summary of total mitigation

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")
library("readxl")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")

options(scipen = 999)
```

## Mitigators included in this analysis

Efficiency mitigators will only impact length of stay and therefore the number of beddays.

Redirection/Substitution, Prevention and Relocation mitigators will affect both the number of admission and also therefore beddays as well.

Virtual Wards mitigators are considered both a relocation mitigator and an efficiency mitigator. 


```{r, fig.height=8, fig.width=10}

mitigator_summary_table<-read_excel("summary_mitigators_table.xlsx")

mitigator_summary_table|>
  select(-mitigator_code, -activity_group)|>
    flextable() |>
    set_header_labels(mitigator_name="Mitigator name",
                      mechanism="Mechanism of mitigation",
                      type_of_admission="Type of admission")|>
    align(part = "header", align = "left") |>
    bg(bg = "#f9bf07", part = "header") |>
    bg( part = "body",
         i = ~ mechanism == "Redirection/Substitution",
        bg="#FCEAAF") |>
      bg( part = "body",
         i = ~ mechanism == "Prevention",
        bg="#FAD9D6" ) |>
      bg( part = "body",
         i = ~ mechanism == "Efficiencies",
        bg="#CDDAEC") |>
       bg( part = "body",
         i = ~ mechanism == "Efficiencies & Relocation",
        bg="#D8DBDC") |>
    bold(bold = TRUE, part = "header") |>
    fontsize(size = 11, part = "body") |>
    fontsize(size = 12, part = "header") |>
    padding(padding = 2,
            part = "all",
            padding.top = NULL) |>
    autofit()
  

```



## Total potential mitigation

#### Admissions

In 2023/24 in England there were .... admissions for potentially mitigable activity. 

NUMBERS BY MECHANISM GROUPS

#### Beddays

In 2023/24 in England there were .... beddays for potentially mitigable activity. 

NUMBERS BY MECHANISM GROUPS

## Cohort overlap

#### Admissions

VENN DIAGRAM OF MECHANISM GROUPS


#### Beddays

VENN DIAGRAM OF MECHANISM GROUPS


## Trend Analysis

We aim to understand whether there have been decreases, or increases, in potentially mitigable activity over time. We have considered total mitigable admissions and beddays over the past 9 years in England as a whole and for each ICB, including: 
a) the absolute number of admissions/beddays,
b) the crude rate of admissions/beddays (i.e. as proportion of total admissions),
c) the age and sex standardised rates of these admissions/beddays using the England 2021 census population.

To help understand the variability between ICBs we have calculated for each ICB the percentage change between 2018/19 and 2023/24.


### England

::: panel-tabset
#### Number over time
::: panel-tabset

#### Admissions
```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_spells_england_all_mitigators
#| fig-cap: The total number of admissions for all mitigable activity in England over the last 9 years. 

numbers_over_time_total_mitigation<-targets::tar_read(numbers_over_time_total_mitigation)|>
  filter(fyear>"201415")

denominator_over_time<-tar_read(denominator_over_time)
icb_population_data<-tar_read(icb_population_data)


number_percentage_over_time<-numbers_over_time_total_mitigation|>
      summarise(episodes=sum(episodes),
              beddays=sum(beddays),
              .by=c(icb_2024_name, year, fyear))|>
      left_join(denominator_over_time|>
                filter(fyear!=201415)|>
                summarise(total_episodes=sum(total_episodes_all),
                total_beddays=sum(total_beddays_all),
                .by=c(fyear, icb_2024_name))
      , by=c("fyear", "icb_2024_name"))|>
    mutate(percentage_episodes=round((episodes/total_episodes)*100,1),
           percentage_beddays=round((beddays/total_beddays)*100,1))|>
    as.data.frame()

plot_of_number_over_time(number_percentage_over_time, episodes)

```
#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_beddays_england_all_mitigators
#| fig-cap: The total number of beddays for all mitigable activity cohort in England over the last 9 years. 
plot_of_number_over_time(number_percentage_over_time,  beddays)


```
:::

#### Crude rate 

Total mitigable activity as a percentage of total elective and emergency admissions/beddays.

::: panel-tabset
#### Admissions
```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_spells_england
#| fig-cap: The percentage of total emergency admissions that are for Frail Elderly High potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>
                               filter(!is.na(percentage_episodes)), episodes, total_episodes)

```
#### Beddays
```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_beddays_england
#| fig-cap: The percentage of total emergency beddays that are for Frail Elderly High potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>
                               filter(!is.na(percentage_beddays)),  beddays, total_beddays)

```

:::


#### Standardised rate over time

::: panel-tabset

#### Admissions
```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_spells_england
#| fig-cap: Age and sex standardised rate of admissions for Frail Elderly High potentially mitigable activity in England over the last 9 years. 

england_age_sex_standardised_rates_episodes<-tar_read(england_age_sex_standardised_rates_episodes)|>
  filter(cohorts=="frail_elderly_high")

plot_of_standardised_rates_over_time(england_age_sex_standardised_rates_episodes)

```

#### Beddays
```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_beddays_england
#| fig-cap: Age and sex standardised rate of beddays for Frail Elderly High potentially mitigable activity in England over the last 9 years.

england_age_sex_standardised_rates_beddays<-tar_read(england_age_sex_standardised_rates_beddays)|>
  filter(cohorts=="frail_elderly_high")

plot_of_standardised_rates_over_time(england_age_sex_standardised_rates_beddays)

```

:::


:::

### ICB

::: panel-tabset

#### Number over time
::: panel-tabset

#### Admissions
```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_spells_icb
#| fig-cap: The number of admissions for the Frail Elderly High mitigable activity cohort by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time|>
        mutate(activity=episodes),
        'Number')

```
#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_beddays_icb
#| fig-cap: The number of beddays for the Frail Elderly High mitigable activity cohort by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time|>
        mutate(activity=beddays), 'Number')
```
:::

#### By proportion of emergency activity 
::: panel-tabset
#### Admissions
```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_spells_icb
#| fig-cap: The percentage of total emergency admissions that are for Frail Elderly High potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time|>
        mutate(activity=percentage_episodes), 'Percentage')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_spells
#| fig-cap: The percentage change in the proportion emergency admissions that are Frail Elderly High admissions by ICB between 2019/20 and 2023/24. 

england_average_percentage_episodes<-calculating_england_average_percentage(number_percentage_over_time, episodes, total_episodes)

plotting_percentage_change_over_time_by_icb(number_percentage_over_time, percentage_episodes, england_average_percentage_episodes$change, 1.6, 1.3)


```


#### Beddays
```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_beddays_icb
#| fig-cap: The percentage of total emergency beddays that are for Frail Elderly High potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time|>
        mutate(activity=percentage_beddays), 'Percentage')

```

<br>


```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_beddays
#| fig-cap: The percentage change in the proportion emergency beddays that are Frail Elderly High beddays by ICB between 2019/20 and 2023/24. 

england_average_percentage_beddays<-calculating_england_average_percentage(number_percentage_over_time, beddays, total_beddays)

plotting_percentage_change_over_time_by_icb(number_percentage_over_time, percentage_beddays, england_average_percentage_beddays$change,  1.6, 1.3)

```

:::


#### Standardised rate over time

::: panel-tabset

#### Admissions
```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_spells_icb
#| fig-cap: Age and sex standardised rate of admissions for Frail Elderly High potentially mitigable activity by ICB over the last 9 years. 

icb_age_sex_standardised_rates_episodes<-tar_read(icb_age_sex_standardised_rates_episodes)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_episodes|> 
     filter(cohorts=="frail_elderly_high")|>
     mutate(activity=value)),
  'Standardised rate per 100,000')

```


<br>


```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_spells
#| fig-cap: The percentage change in the standardised rate of Frail Elderly High admissions by ICB between 2019/20 and 2023/24. 

england_average_standardised_episodes<-calculating_england_average_standardised(england_age_sex_standardised_rates_episodes)

plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_episodes, value, england_average_standardised_episodes$change, 1.3, 1.7)

```

#### Beddays
```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_beddays_icb
#| fig-cap: Age and sex standardised rate of beddays for Frail Elderly High potentially mitigable activity by ICB over the last 9 years.

icb_age_sex_standardised_rates_beddays<-tar_read(icb_age_sex_standardised_rates_beddays)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_beddays|> 
     filter(cohorts=="frail_elderly_high")|>
     mutate(activity=value)),
  'Standardised rate per 100,000')

```


<br>


```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_beddays
#| fig-cap: The percentage change in the standardised rate of Frail Elderly High beddays by ICB between 2019/20 and 2023/24. 


england_average_standardised_beddays<-calculating_england_average_standardised(england_age_sex_standardised_rates_beddays)

plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_beddays, value, england_average_standardised_beddays$change, 1.4, 1.6)


```

:::

:::

## Comparative Analysis

This section is still a work in progress.

:::panel-tabset

### Admissions

```{r}
#| output: false
summary_frail_elderly_high_icb_admissions <- targets::tar_read(summary_frail_elderly_high_icb_admissions)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names()

number_frail_elderly_high_icb_admissions_map <- summary_frail_elderly_high_icb_admissions |>
  get_summary_by_icb_map(icb_23_shp, "total_count")

perc_frail_elderly_high_icb_admissions_map <- summary_frail_elderly_high_icb_admissions |>
  get_summary_by_icb_map(icb_23_shp, "perc")

rate_frail_elderly_high_icb_admissions_map <- summary_frail_elderly_high_icb_admissions |>
  get_summary_by_icb_map(icb_23_shp, "value")
```

:::panel-tabset

#### Number of admissions

:::panel-tabset

##### Bars

```{r}
#| label: fig-number_frail_elderly_high_icb_admissions_bar
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "number", "admissions")
england_value <- get_england_value("total_count", 
                                   data_number = summary_frail_elderly_high_icb_admissions)

get_summary_by_icb_bar(summary_frail_elderly_high_icb_admissions, 
                       "total_count", 
                       "frail_elderly_high",
                       england_value)

rm(england_value)
```

##### Map

```{r}
#| label: fig-number_frail_elderly_high_icb_admissions_map
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "number", "admissions")
number_frail_elderly_high_icb_admissions_map
```

:::

#### Percentage of emergency activity

:::panel-tabset

##### Bars

```{r}
#| label: fig-perc_frail_elderly_high_icb_admissions_bar
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "perc", "admissions")
total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

england_value <- get_england_value("perc", 
                                   activity = "admissions",
                                   treatment = "emergency",
                                   data_rate = england_age_sex_standardised_rates_episodes,
                                   cohort = "frail_elderly_high")

get_summary_by_icb_bar(summary_frail_elderly_high_icb_admissions, 
                       "perc", 
                       "frail_elderly_high",
                       england_value)

rm(england_value)
```

##### Map

```{r}
#| label: fig-perc_frail_elderly_high_icb_admissions_map
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "perc", "admissions", "emergency")
perc_frail_elderly_high_icb_admissions_map
```

:::

#### Age and sex standardised rates per 100,000 population

:::panel-tabset

##### Bars

```{r}
#| label: fig-rate_frail_elderly_high_icb_admissions_bar
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "SR", "admissions")
england_value <- get_england_value("value",
                                   data_rate = england_age_sex_standardised_rates_episodes,
                                   cohort = "frail_elderly_high")

get_summary_by_icb_bar(summary_frail_elderly_high_icb_admissions, 
                       "value", 
                       "frail_elderly_high",
                       england_value)

rm(england_value)
```

##### Map

```{r}
#| label: fig-rate_frail_elderly_high_icb_admissions_map
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "SR", "admissions")
rate_frail_elderly_high_icb_admissions_map
```

:::

#### Table

```{r}
#| label: tbl-rate_frail_elderly_high_icb_admissions
#| tbl-cap: !expr get_caption_by_icb_table("Frail Elderly (high)", "admissions", "emergency")
get_summary_by_icb_table(summary_frail_elderly_high_icb_admissions, "episodes", "emergency")
```

:::

### Beddays

Coming soon. Want to get content right for admissions first.

:::

