# Potentially mitigable activity {#sec-summary .unnumbered}

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")
library("readxl")
library("ggVennDiagram")
library("stringr")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")
source("R/manipulating_mitigators_and_mechanisms.R")

options(scipen = 999)

numbers_over_time<-tar_read(numbers_over_time)
numbers_over_time_total_mitigation<-targets::tar_read(numbers_over_time_total_mitigation)|>
  filter(fyear>"201415")
total_cohort_numbers_2324<-tar_read(total_cohort_numbers_2324)
icb_population_data<-tar_read(icb_population_data)
denominator_over_time<-tar_read(denominator_over_time)
england_age_sex_standardised_rates_beddays_total_mitigation<-tar_read(england_age_sex_standardised_rates_beddays_total_mitigation)
england_age_sex_standardised_rates_episodes_total_mitigation<-tar_read(england_age_sex_standardised_rates_episodes_total_mitigation)
```

```{r global variables}
cohort <- "all"
cohort_title <- "All Mitigation"
treatment_type <- "both"
treatment_type_title <- format_treatment_for_caption(treatment_type)
```

```{r}
number_percentage_over_time<-numbers_over_time_total_mitigation|>
  left_join(denominator_over_time, by=c("age_range", "sex", "year", "icb", "icb_2024_name"))|>
  summarise(episodes=janitor::round_half_up(sum(episodes, na.rm=TRUE),0),
            beddays=janitor::round_half_up(sum(beddays, na.rm=TRUE),0),
            total_episodes=sum(total_episodes_all, na.rm=TRUE),
            total_beddays=sum(total_beddays_all, na.rm=TRUE),
            .by=c(icb, icb_2024_name, year))|>
  filter(year!="2014/15")|>
  mutate(percentage_episodes=janitor::round_half_up((episodes/total_episodes)*100,1),
         percentage_beddays=janitor::round_half_up((beddays/total_beddays)*100,1))|>
  as.data.frame()
```

Methods of classifying acute activity  as ‘potentially mitigable’ were developed as part of the Strategy Unit’s work on the New Hospital Programme (NHP). All activity that meets the criteria for potentially mitigable is included within the mitigator cohorts, but in practice, only a proportion of this activity would be truly mitigable. 

In this suite of reports, we apply our methods of identifying potentially mitigable hospital activity to all NHS trusts in England. These reports then allow users to explore potentially mitigable activity in greater depth; to understand patient and admission characteristics; to understand where activity falls into more than one type of mitigator; how rates compare by ICB; and how they have changed over time. 

By necessity, the size of ‘potentially mitigable’ activity is large. Often this is because definitions themselves are extremely broad. For example, the mitigator for Frail and Older People Admissions is defined as any emergency admission for a patient aged 75 or over where that person also has a certain level of frailty – a large proportion of NHS activity which is by no means entirely or even largely mitigable. It is hoped that further research and analysis in this area will lead to improvements in the criteria used to define potentially mitigable activity. Thus providing greater clarity on defining the acute care which is more likely to be legitimately mitigable.


Here, we provide information for 29 mitigators - the NHP Demand and Capacity Tool includes 92 in total - chosen as those which impact emergency admissions and bed days and are amenable to interventions from other healthcare services such as community services and primary care. Each of the mitigators falls under one of four ‘mechanisms’ for mitigation. These mechanisms are i) Redirection/Substitution, ii) Prevention, iii) Relocation & Efficiencies and iv) Efficiencies (seeking only reduction in bed days and not initial admissions). Our suite of reports provides summaries for each mechanism with further pages for each individual mitigator.



## Mitigable activity

The numbers of admissions and beddays give the potentially mitigable activity for England in 2023/24, for each mechanism of mitigation group and in total.

#### Number of admissions and beddays for each mechanism of mitigation

```{r}
total_mitigator_activity <- numbers_over_time_total_mitigation |>
  filter(year == "2023/24") |>
  summarise(episodes = sum(episodes), beddays = sum(beddays)) |>
  dplyr::mutate(mechanism = "Total potential mitigable activity", 
                .before = "episodes")

total_cohort_numbers_2324 |>
  generate_data_for_mechanism_cohort_overlaps() |>
  gather(key = mechanism, value = value, -episodes, -beddays) |>
  filter(value != 0) |>
  summarise(
    episodes = sum(episodes),
    beddays = sum(beddays),
    .by = mechanism
  ) |>
  mutate(episodes = ifelse(mechanism == "Efficiencies", NA, episodes)) |>
  rbind(total_mitigator_activity) |>
  flextable() |>
  set_header_labels(episodes = "Admissions",
                    beddays = "Beddays",
                    mechanism = "Mechanism of mitigation") |>
  align(part = "header", align = "left") |>
  bg(bg = "#f9bf07", part = "header") |>
  bold(bold = TRUE, part = "header") |>
  fontsize(size = 10, part = "body") |>
  fontsize(size = 11, part = "header") |>
  padding(padding = 2,
          part = "all",
          padding.top = NULL) |>
  autofit() |>
  flextable::hline(i = 4, border = flextable::fp_border_default())
```

NOTE: The sum of all the admissions and beddays for each mechanism does not add up to the total potential mitigable activity, as much of the activity is included within more than one mechanism of mitigation group and and thus adding the numbers for each group will lead to double counting. The numbers provided for the total potential mitigable activity excludes any double counting as a result of activity being including in multiple mitigator cohorts.

## Overlap between the mechanism of mitigation groups

Many admissions meet the criteria to be included in more than one mechanism of mitigation group. Since these potential mechanism of mitigation groups are not mutually exclusive there is a need to understand which groups overlap and the degree of overlap between the cohorts.

:::panel-tabset

#### Admissions

::: columns
::: {.column width="70%"}
```{r, fig.width=4, fig.height=4}
#| label: fig-overlap_mechanism_cohorts_episodes
#| fig-cap: Venn diagram showing the overlap in admissions between the mechanisms of mitigation groups.

total_cohort_numbers_2324<-tar_read(total_cohort_numbers_2324)

generate_venn_diagram(total_cohort_numbers_2324, episodes)

```
:::

::: {.column width="30%"}
```{r, fig.width=3, fig.height=4}
#| label: fig-number_of_mechanism_groups_episodes
#| fig-cap: Number of mechanism groups the admissions are a part of.

plotting_barchart_number_of_mechanism_groups(total_cohort_numbers_2324, episodes)

```
:::

NB: Efficiency mitigators do not impact the number of admissions, only the length of stay, hence they do not overlap in terms of admissions with the other cohorts.
:::

The majority of mitigable admissions (57%) are purely for activity where there could be redirection to perhaps community services. 

Over three quarters of mitigable admissions fall into just one mechanism of mitigation group.

#### Beddays

::: columns
::: {.column width="70%"}
```{r, fig.width=7, fig.height=4}
#| label: fig-overlap_mechanism_cohorts_beddays
#| fig-cap: Venn diagram showing the overlap in beddays between the mechanisms of mitigation groups.

generate_venn_diagram(total_cohort_numbers_2324, beddays)

```
:::

::: {.column width="30%"}
```{r, fig.width=3, fig.height=4}
#| label: fig-number_of_mechanism_groups_beddays
#| fig-cap: Number of mechanism groups the beddays are a part of.

plotting_barchart_number_of_mechanism_groups(total_cohort_numbers_2324, beddays)

```
:::
:::

The majority of mitigable beddays are included in multiple mechanism of mitigation groups, only 10% of mitgable beddays falling within a single mechanism group. 

One third of mitigable beddays are included with 3 mechanism of mitigation groups (Redirection/Substitution, Prevention and Efficiencies)

:::
## Comparative Analysis


```{r}
#| output: false
summary_icb_admissions_all <- targets::tar_read(summary_icb_admissions_all)
summary_icb_beddays_all <- targets::tar_read(summary_icb_beddays_all)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names() |>
  dplyr::mutate(icb23nm = simplify_icb_name(icb23nm))

number_icb_admissions_all_map <- summary_icb_admissions_all |>
  get_summary_by_icb_map(icb_23_shp, "total_count")

perc_icb_admissions_all_map <- summary_icb_admissions_all |>
  get_summary_by_icb_map(icb_23_shp, "perc")

rate_icb_admissions_all_map <- summary_icb_admissions_all |>
  get_summary_by_icb_map(icb_23_shp, "value")

number_icb_beddays_all_map <- summary_icb_beddays_all |>
  get_summary_by_icb_map(icb_23_shp, "total_count")

perc_icb_beddays_all_map <- summary_icb_beddays_all |>
  get_summary_by_icb_map(icb_23_shp, "perc")

rate_icb_beddays_all_map <- summary_icb_beddays_all |>
  get_summary_by_icb_map(icb_23_shp, "value")
```

### Integrated Care Board
::: panel-tabset
#### Number

::: panel-tabset
##### Bars

::: panel-tabset
###### Admissions
```{r}
#| label: fig-number_icb_admissions_all_bar
#| fig-cap: !expr get_caption_by_geography(cohort_title, "number", "admissions")
england_value <- get_england_value(
  "total_count", 
  data = summary_icb_admissions_all)

get_summary_by_icb_bar(
  summary_icb_admissions_all, 
  "total_count", 
  cohort,
  england_value)

rm(england_value)

```

###### Beddays
```{r}
#| label: fig-number_icb_beddays_all_bar
#| fig-cap: !expr get_caption_by_geography(cohort_title, "number", "beddays")
england_value <- get_england_value(
  "total_count", 
  data = summary_icb_beddays_all)

get_summary_by_icb_bar(
  summary_icb_beddays_all, 
  "total_count", 
  cohort,
  england_value)

rm(england_value)
```
:::

##### Map

::: panel-tabset
###### Admissions
```{r}
#| label: fig-number_icb_admissions_all_map
#| fig-cap: !expr get_caption_by_geography(cohort_title, "number", "admissions")
number_icb_admissions_all_map
```

###### Beddays
```{r}
#| label: fig-number_icb_beddays_all_map
#| fig-cap: !expr get_caption_by_geography(cohort_title, "number", "beddays")
number_icb_beddays_all_map
```
:::
:::

#### Percentage of `r treatment_type_title` activity

::: panel-tabset
##### Bars

::: panel-tabset
###### Admissions
```{r}
#| label: fig-perc_icb_admissions_all_bar
#| fig-cap: !expr get_caption_by_geography(cohort_title, "perc", "admissions", treatment_type)
total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

england_value <- get_england_value(
  "perc_total_mitigation",
  activity = "admissions",
  treatment = treatment_type,
  data = number_percentage_over_time)

get_summary_by_icb_bar(
  summary_icb_admissions_all, 
  "perc", 
  cohort,
  england_value)

rm(england_value)
```

###### Beddays
```{r}
#| label: fig-perc_icb_beddays_all_bar
#| fig-cap: !expr get_caption_by_geography(cohort_title, "perc", "beddays", treatment_type)

england_value <- get_england_value(
  "perc_total_mitigation",
  activity = "beddays",
  treatment = treatment_type,
  data = number_percentage_over_time)

get_summary_by_icb_bar(
  summary_icb_beddays_all,
  "perc",
  cohort,
  england_value)

rm(england_value)
```
:::

##### Map

::: panel-tabset
###### Admissions
```{r}
#| label: fig-perc_icb_admissions_all_map
#| fig-cap: !expr get_caption_by_geography(cohort_title, "perc", "admissions", treatment_type)
perc_icb_admissions_all_map
```

###### Beddays
```{r}
#| label: fig-perc_icb_beddays_all_map
#| fig-cap: !expr get_caption_by_geography(cohort_title, "perc", "beddays", treatment_type)
perc_icb_beddays_all_map
```
:::
:::

#### Age and sex standardised rates per 100,000 population

::: panel-tabset
##### Bars

::: panel-tabset
###### Admissions
```{r}
#| label: fig-rate_icb_admissions_all_bar
#| fig-cap: !expr get_caption_by_geography(cohort_title, "SR", "admissions")
england_value <- get_england_value(
  "value",
  data = england_age_sex_standardised_rates_episodes_total_mitigation,
  cohort = cohort)

get_summary_by_icb_bar(
  summary_icb_admissions_all, 
  "value", 
  cohort,
  england_value)

rm(england_value)
```

###### Beddays
```{r}
#| label: fig-rate_icb_beddays_all_bar
#| fig-cap: !expr get_caption_by_geography(cohort_title, "SR", "beddays")
england_value <- get_england_value(
  "value",
  data = england_age_sex_standardised_rates_beddays_total_mitigation,
  cohort = cohort)

get_summary_by_icb_bar(
  summary_icb_beddays_all,
  "value",
  cohort,
  england_value)

rm(england_value)
```
:::

##### Map

::: panel-tabset
###### Admissions
```{r}
#| label: fig-rate_icb_admissions_all_map
#| fig-cap: !expr get_caption_by_geography(cohort_title, "SR", "admissions")
rate_icb_admissions_all_map
```

###### Beddays
```{r}
#| label: fig-rate_icb_beddays_all_map
#| fig-cap: !expr get_caption_by_geography(cohort_title, "SR", "beddays")
rate_icb_beddays_all_map
```
:::
:::

#### Table

::: panel-tabset
###### Admissions
```{r}
#| label: tbl-rate_icb_admissions_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "admissions", treatment_type, "icb")
get_summary_by_geography_table(
  summary_icb_admissions_all,
  "episodes", 
  treatment_type)
```

###### Beddays
```{r}
#| label: tbl-rate_icb_beddays_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "beddays", treatment_type, "icb")
get_summary_by_geography_table(
  summary_icb_beddays_all, 
  "beddays", 
  treatment_type)
```
:::
:::

### Local Authority
::: panel-tabset

#### Admissions
```{r}
#| label: tbl-rate_la_admissions_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "admissions", treatment_type, "la")
targets::tar_read(summary_la_admissions_all) |>
  get_summary_by_geography_table("episodes",
                                 treatment_type)
```

#### Beddays
```{r}
#| label: tbl-rate_la_beddays_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "beddays", treatment_type, "la")
targets::tar_read(summary_la_beddays_all) |>
  get_summary_by_geography_table("beddays", treatment_type)
```

:::

## Trend Analysis

We aim to understand whether there have been decreases, or increases, in potentially mitigable activity over time. We have considered total mitigable admissions and beddays over the past 9 years in England as a whole and for each ICB, including:

a\) the absolute number of admissions/beddays,

b\) these admissions/beddays as a proportion of total admissions,

c\) the age and sex standardised rates of these admissions/beddays using the England 2021 census population.

To help understand the variability between ICBs we have calculated for each ICB the percentage change between 2018/19 and 2023/24.

### England

::: panel-tabset
#### Number over time

```{r}
# England average numbers and % change
england_average_numbers_episodes<-calculating_england_average_numbers(number_percentage_over_time, episodes)

england_average_numbers_beddays<-calculating_england_average_numbers(number_percentage_over_time, beddays)

# England average percentages and % change
england_average_percentage_beddays<-calculating_england_average_percentage(number_percentage_over_time|>filter(!is.nan(percentage_episodes)), beddays, total_beddays)

england_average_percentage_episodes<-calculating_england_average_percentage(number_percentage_over_time|>filter(!is.nan(percentage_episodes)), episodes, total_episodes)


# England standardised rate and % change
england_average_standardised_episodes_total_mitigation<-calculating_england_average_standardised(england_age_sex_standardised_rates_episodes_total_mitigation)


england_average_standardised_beddays_total_mitigation<-calculating_england_average_standardised(england_age_sex_standardised_rates_beddays_total_mitigation)

```

Over the last 5 years (2018/19 to 2023/24), there has been a `r england_average_numbers_episodes$change` % in the percentage of admissions that are for potentially mitigable activity and a `r england_average_numbers_beddays$change` % increase in the percentage of beddays that are for potentially mitigable activity.

::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_spells_england_all_mitigators
#| fig-cap: The number of admissions for all mitigable activity in England over the last 9 years.

plot_of_number_over_time(number_percentage_over_time, episodes)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_beddays_england_all_mitigators
#| fig-cap: The number of beddays for all mitigable activity cohort in England over the last 9 years. 
plot_of_number_over_time(number_percentage_over_time,  beddays)

```
:::

#### Percentage of total activity

Total mitigable activity as a percentage of total activity (elective and emergency admissions/beddays).

Over the last 5 years (2018/19 to 2023/24), there has been a `r england_average_percentage_episodes$change` % increase in potentially mitigable admissions and a `r england_average_percentage_beddays$change` % increase in potentially mitigable beddays.

::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_spells_england
#| fig-cap: The percentage of admissions for potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>          filter(!is.na(percentage_episodes)), episodes, total_episodes)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_beddays_england
#| fig-cap: The percentage of beddays for potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>
                               filter(!is.na(percentage_beddays)),  beddays, total_beddays)

```
:::

#### Age and sex standardised rates per 100,000 population

Over the last 5 years (2018/19 to 2023/24), when accounting for changes in the population age and sex, there has been a `r england_average_standardised_episodes_total_mitigation$change` % increase in potentially mitigable admissions. However, there has been a `r england_average_standardised_beddays_total_mitigation$change` % decrease in potentially mitigable beddays, suggesting reduced length of stays for mitigable activity.


::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_spells_england
#| fig-cap: Age and sex standardised rate of potentially mitigable admissions in England over the last 9 years. 


plot_of_standardised_rates_over_time(
  england_age_sex_standardised_rates_episodes_total_mitigation)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_beddays_england
#| fig-cap: Age and sex standardised rate of potentially mitigable beddays in England over the last 9 years.

plot_of_standardised_rates_over_time(
  england_age_sex_standardised_rates_beddays_total_mitigation)

```
:::
:::

### Integrated Care Board

Total potentially mitigable activity over time is shown for each ICB to demonstrate the patterns of change and the degree of variability between ICBs over time. The percentage change in total potentially mitigable activity between 2018/19 and 2023/24 is compared across ICBs and shown relative to the England average. 

Note: Low numbers of admissions/beddays for Frimley ICB in 2022/23 reflect an issue with data submissions for this period.

::: panel-tabset
#### Number over time

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_spells_icb
#| fig-cap: The number of admissions for all potentially mitigable activity by ICB over the last 9 years. 

number_percentage_over_time_removing_icb_na<-number_percentage_over_time|>
  filter(!is.na(icb_2024_name))


plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
        mutate(activity=episodes),
        'Number')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_spells
#| fig-cap: The percentage change in the number of potentially mitigable admissions by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(number_percentage_over_time|>filter(!is.na(icb_2024_name)), episodes, icb_2024_name , england_average_numbers_episodes$change, 1.3, 1.3)

```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_beddays_icb
#| fig-cap: The number of beddays for all potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
        mutate(activity=beddays), 'Number')
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_beddays
#| fig-cap: The percentage change in the number of potentially mitigable beddays by ICB between 2018/19 and 2023/24. 

plotting_percentage_change_over_time_by_icb(number_percentage_over_time|>filter(!is.na(icb_2024_name)), beddays, icb_2024_name, england_average_numbers_beddays$change, 1.3, 1.3)

```
:::

#### Percentage of total activity

Total mitigable activity as a percentage of total elective and emergency admissions/beddays.

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_spells_icb
#| fig-cap: The percentage of admissions for potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
            filter(!is.nan(percentage_episodes))|>
        mutate(activity=percentage_episodes), 'Percentage')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_spells
#| fig-cap: The percentage change in the proportion emergency admissions that are for potentially mitigable admissions by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(number_percentage_over_time_removing_icb_na, percentage_episodes, icb_2024_name, england_average_percentage_episodes$change, 2.3, 1.3)


```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_beddays_icb
#| fig-cap: The percentage of beddays for potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
              filter(!is.nan(percentage_beddays))|>
        mutate(activity=percentage_beddays), 'Percentage')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_beddays
#| fig-cap: The percentage change in the proportion emergency beddays that are for potentially mitigable beddays by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(number_percentage_over_time_removing_icb_na, percentage_beddays, icb_2024_name, england_average_percentage_beddays$change,  1.6, 1.3)

```
:::

#### Age and sex standardised rates per 100,000 population

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_spells_icb
#| fig-cap: Age and sex standardised rate of potentially mitigable admissions by ICB over the last 9 years. 

icb_age_sex_standardised_rates_episodes_total_mitigation<-tar_read(icb_age_sex_standardised_rates_episodes_total_mitigation)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_episodes_total_mitigation|> 
     mutate(activity=value)),
  'Standardised rate per 100,000')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_spells
#| fig-cap: The percentage change in the standardised rate of potentially mitigable admissions by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_episodes_total_mitigation, value, icb_2024_name, england_average_standardised_episodes_total_mitigation$change, 1.3, 1.2)

```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_beddays_icb
#| fig-cap: Age and sex standardised rate of potentially mitigable beddays by ICB over the last 9 years.

icb_age_sex_standardised_rates_beddays_total_mitigation<-tar_read(icb_age_sex_standardised_rates_beddays_total_mitigation)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_beddays_total_mitigation|> 
     mutate(activity=value)),
  'Standardised rate per 100,000')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_beddays
#| fig-cap: The percentage change in the standardised rate of potentially mitigable beddays by ICB between 2018/19 and 2023/24. 

plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_beddays_total_mitigation, value,icb_2024_name, england_average_standardised_beddays_total_mitigation$change, 1.3, 1.3)


```
:::
:::

#### Change in standardised rate relative over the last 5 years, relative to the starting rate in 2018/19, by ICB.

This chart shows the percentage change in the age and sex standardised rate per 100,000 population for each ICB (between 2018/19 and 2023/24) relative to it's starting rate in 2018/19, to help demonstrate performance across ICBs. 

Those ICBs in the lower left quadrant (shaded in green) could be considered as performing well; they already had relatively low standardised rates of admissions/beddays in 2018/19 and have continued to make further decreases over the last five years.

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_episodes
#| fig-cap: The standardised rate of potentially mitigable admissions (in 2018/19) versus the percentage change in admissions between 2018/19 and 2023/24 for ICBs. 

plotting_total_activity_vs_percentage_change(icb_age_sex_standardised_rates_episodes_total_mitigation, icb_2024_name)


```

#### Beddays

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_beddays
#| fig-cap: The standardised rate of potentially mitigable beddays (in 2018/19) versus the percentage change in beddays between 2018/19 and 2023/24 for ICBs. 
#| 
plotting_total_activity_vs_percentage_change(icb_age_sex_standardised_rates_beddays_total_mitigation, icb_2024_name)


```
:::


### Local Authority

Age and sex standardised rates of activity per 100,000 population for local authority areas. 

::: panel-tabset

#### Admissions
```{r}
#| label: table-local_authority_over_time_episodes
#| fig-cap: Table of the standardised rate of all potentially mitigable admissions by Local Authority over the last 5 years, including the percentage change between 2018/19 and 2023/24.  

la_age_sex_standardised_rates_episodes_total_mitigation<-tar_read(la_age_sex_standardised_rates_episodes_total_mitigation)

la_episode_table<-generating_la_table(la_age_sex_standardised_rates_episodes_total_mitigation, cohort)
 
DT::datatable(la_episode_table)


```


#### Beddays
```{r}
#| label: table_local_authority_over_time_beddays
#| fig-cap: Table of the standardised rate of all potentially mitigable beddays by Local Authority over the last 5 years, including the percentage change between 2018/19 and 2023/24.  

la_age_sex_standardised_rates_beddays_total_mitigation<-tar_read(la_age_sex_standardised_rates_beddays_total_mitigation)

la_beddays_table<-generating_la_table(la_age_sex_standardised_rates_beddays_total_mitigation, cohort)
 
DT::datatable(la_beddays_table)

```

:::
