# Summary of total mitigation {#sec-summary .unnumbered}

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")
library("readxl")
library("ggVennDiagram")
library("stringr")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")

options(scipen = 999)

numbers_over_time<-tar_read(numbers_over_time)
numbers_over_time_total_mitigation<-targets::tar_read(numbers_over_time_total_mitigation)|>
  filter(fyear>"201415")
total_cohort_numbers_2324<-tar_read(total_cohort_numbers_2324)
```

## Mitigators included in this analysis

Numbers of admissions and beddays give the potentially mitigable activity for England in 2023/24.

Redirection/Substitution, Prevention and Relocation mitigators will affect both the number of admission and also therefore also impact beddays.

Efficiency mitigators will only impact length of stay and therefore the number of beddays.

Virtual Wards mitigators are considered both a relocation mitigator and an efficiency mitigator.

```{r, fig.height=8, fig.width=10}

mitigator_summary_table<-read_excel("summary_mitigators_table.xlsx")|>
  left_join(numbers_over_time|>
              filter(year=="2023/24")|>
              summarise(episodes=sum(episodes),
                        beddays=sum(beddays),
                        .by=cohorts), by=c("mitigator_code"="cohorts"))|>
  select(-activity_group, -mitigator_code)|>
    mutate(episodes=ifelse(mechanism=="Efficiencies", NA, episodes))|>
  rename(`Mechanism of mitigation`=mechanism)


mitigator_summary_table|>
  as_grouped_data(groups = "Mechanism of mitigation")|>
  as_flextable() |>
    set_header_labels(mitigator_name="Mitigator name",
                      type_of_admission="Type of admission",
                      episodes="Admissions",
                      beddays="Beddays")|>
    align(part = "header", align = "left") |>
    bg(bg = "#f9bf07", part = "header") |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Redirection/Substitution") |>
        bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Redirection/Substitution",
        bg="#D8DBDC" ) |>
      bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Prevention",
        bg="#D8DBDC" ) |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Prevention") |>
      bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies",
        bg="#D8DBDC") |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies") |>
       bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies & Relocation",
        bg="#D8DBDC") |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies & Relocation") |>
    bold(bold = TRUE, part = "header") |>
    fontsize(size = 10, part = "body") |>
    fontsize(size = 11, part = "header") |>
    padding(padding = 2,
            part = "all",
            padding.top = NULL) |>
    autofit()
  

```

NOTE: The sum of all the individual mitigator activity in this table does not add up to the total potential mitigable activity. This is because much of the activity is by included within multiple different mitigator cohorts and thus adding the total for each mitigator will lead to double counting of admissions and beddays.

## Potential mitigable activity for England in 2023/24

```{r}
total_mitigator_activity<-numbers_over_time_total_mitigation|>
  filter(year=="2023/24")|>
  summarise(episodes=sum(episodes),
            beddays=sum(beddays))

```

**In 2023/24 in England there were `r format(total_mitigator_activity$episodes, big.mark=",")` admissions and `r format(total_mitigator_activity$beddays, big.mark=",")` beddays for potentially mitigable activity.**

```{r}
total_cohort_numbers_2324|>
  generate_data_for_mechanism_cohort_overlaps()|>
  gather(key=mechanism, value=value, -episodes, -beddays)|>
  filter(value!=0)|>
  summarise(episodes=sum(episodes),
            beddays=sum(beddays),
                        .by=mechanism) |>
  mutate(episodes=ifelse(mechanism=="Efficiencies", NA, episodes))|>
  flextable() |>
    set_header_labels(episodes="Admissions",
                      beddays="Beddays",
                      mechanism="Mechanism of mitgation")|>
    align(part = "header", align = "left") |>
    bg(bg = "#f9bf07", part = "header") |>
    bold(bold = TRUE, part = "header") |>
    fontsize(size = 10, part = "body") |>
    fontsize(size = 11, part = "header") |>
    padding(padding = 2,
            part = "all",
            padding.top = NULL) |>
    autofit()
  

```



## Cohort overlap

#### Admissions

::: columns

::: {.column width="70%"}

```{r, fig.width=4, fig.height=4}
#| label: fig-overlap_mechanism_cohorts_episodes
#| fig-cap: Venn diagram showing the overlap in admissions between the mechanisms of mitigation groups.

total_cohort_numbers_2324<-tar_read(total_cohort_numbers_2324)

generate_venn_diagram(total_cohort_numbers_2324, episodes)

```
:::

::: {.column width="30%"}

```{r, fig.width=3, fig.height=4}
#| label: fig-number_of_mechanism_groups_episodes
#| fig-cap: Number of mechanism groups the admissions are a part of.

plotting_barchart_number_of_mechanism_groups(total_cohort_numbers_2324, episodes)

```

:::

NB: Efficiency mitigators do not impact the number of admissions, only the length of stay, hence they do not overlap in terms of admissions with the other cohorts.

:::


#### Beddays

::: columns

::: {.column width="70%"}

```{r, fig.width=7, fig.height=4}
#| label: fig-overlap_mechanism_cohorts_beddays
#| fig-cap: Venn diagram showing the overlap in beddays between the mechanisms of mitigation groups.

generate_venn_diagram(total_cohort_numbers_2324, beddays)

```
:::

::: {.column width="30%"}
```{r, fig.width=3, fig.height=4}
#| label: fig-number_of_mechanism_groups_beddays
#| fig-cap: Number of mechanism groups the beddays are a part of.

plotting_barchart_number_of_mechanism_groups(total_cohort_numbers_2324, beddays)

```
:::
:::


## Comparative Analysis

TO BE CHANGED TO TOTAL MITIGATION

::: panel-tabset
### Admissions

```{r}
#| output: false
summary_icb_admissions_frail_elderly_high <- targets::tar_read(summary_icb_admissions_frail_elderly_high)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names()

number_icb_admissions_frail_elderly_high_map <- summary_icb_admissions_frail_elderly_high |>
  get_summary_by_icb_map(icb_23_shp, "total_count")

perc_icb_admissions_frail_elderly_high_map <- summary_icb_admissions_frail_elderly_high |>
  get_summary_by_icb_map(icb_23_shp, "perc")

rate_icb_admissions_frail_elderly_high_map <- summary_icb_admissions_frail_elderly_high |>
  get_summary_by_icb_map(icb_23_shp, "value")
```

::: panel-tabset
#### Number of admissions

::: panel-tabset
##### Bars

```{r}
#| label: fig-number_icb_admissions_frail_elderly_high_bar
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "number", "admissions")
england_value <- get_england_value("total_count", 
                                   data_number = summary_icb_admissions_frail_elderly_high)

get_summary_by_icb_bar(summary_icb_admissions_frail_elderly_high, 
                       "total_count", 
                       "frail_elderly_high",
                       england_value)

rm(england_value)
```

##### Map

```{r}
#| label: fig-number_icb_admissions_frail_elderly_high_map
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "number", "admissions")
number_icb_admissions_frail_elderly_high_map
```
:::

#### Percentage of emergency activity

::: panel-tabset
##### Bars

```{r, eval=FALSE}
#| label: fig-perc_icb_admissions_frail_elderly_high_bar
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "perc", "admissions")
total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

england_value <- get_england_value("perc", 
                                   activity = "admissions",
                                   treatment = "emergency",
                                   data_rate = england_age_sex_standardised_rates_episodes,
                                   cohort = "frail_elderly_high")

get_summary_by_icb_bar(summary_icb_admissions_frail_elderly_high, 
                       "perc", 
                       "frail_elderly_high",
                       england_value)

rm(england_value)
```

##### Map

```{r}
#| label: fig-perc_icb_admissions_frail_elderly_high_map
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "perc", "admissions", "emergency")
perc_icb_admissions_frail_elderly_high_map
```
:::

#### Age and sex standardised rates per 100,000 population

::: panel-tabset
##### Bars

```{r, eval=FALSE}
#| label: fig-rate_icb_admissions_frail_elderly_high_bar
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "SR", "admissions")
england_value <- get_england_value("value",
                                   data_rate = england_age_sex_standardised_rates_episodes,
                                   cohort = "frail_elderly_high")

get_summary_by_icb_bar(summary_icb_admissions_frail_elderly_high, 
                       "value", 
                       "frail_elderly_high",
                       england_value)

rm(england_value)
```

##### Map

```{r}
#| label: fig-rate_icb_admissions_frail_elderly_high_map
#| fig-cap: !expr get_caption_by_icb("Frail Elderly (high)", "SR", "admissions")
rate_icb_admissions_frail_elderly_high_map
```
:::

#### Table

```{r}
#| label: tbl-rate_icb_admissions_frail_elderly_high
#| tbl-cap: !expr get_caption_by_geography_table("Frail Elderly (high)", "admissions", "emergency", "icb")
get_summary_by_geography_table(summary_icb_admissions_frail_elderly_high, "episodes", "emergency")
```
:::

### Beddays

Coming soon. Want to get content right for admissions first.
:::


## Trend Analysis

We aim to understand whether there have been decreases, or increases, in potentially mitigable activity over time. We have considered total mitigable admissions and beddays over the past 9 years in England as a whole and for each ICB, including:

a\) the absolute number of admissions/beddays,

b\) the crude rate of admissions/beddays (i.e. as proportion of total admissions),

c\) the age and sex standardised rates of these admissions/beddays using the England 2021 census population.

To help understand the variability between ICBs we have calculated for each ICB the percentage change between 2018/19 and 2023/24.

### England

::: panel-tabset
#### Number over time

::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_spells_england_all_mitigators
#| fig-cap: The number of admissions for all mitigable activity in England over the last 9 years. 

denominator_over_time<-tar_read(denominator_over_time)|>
  filter(age_range!="NA")
icb_population_data<-tar_read(icb_population_data)


denominator_over_time<-tar_read(denominator_over_time)


number_percentage_over_time<-numbers_over_time_total_mitigation|>
  left_join(denominator_over_time, by=c("age_range", "sex", "year", "icb", "icb_2024_name"))|>
  summarise(episodes=sum(episodes, na.rm=TRUE),
            beddays=sum(beddays, na.rm=TRUE),
            total_episodes=sum(total_episodes_all, na.rm=TRUE),
            total_beddays=sum(total_beddays_all, na.rm=TRUE),
            .by=c(icb, icb_2024_name, year))|>
  filter(year!="2014/15")|>
  mutate(percentage_episodes=round((episodes/total_episodes)*100,1),
         percentage_beddays=round((beddays/total_beddays)*100,1))|>
  as.data.frame()

plot_of_number_over_time(number_percentage_over_time, episodes)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_beddays_england_all_mitigators
#| fig-cap: The number of beddays for all mitigable activity cohort in England over the last 9 years. 
plot_of_number_over_time(number_percentage_over_time,  beddays)


```
:::

#### Crude rate

Total mitigable activity as a percentage of total activity (elective and emergency admissions/beddays).

::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_spells_england
#| fig-cap: The percentage of admissions for potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>
                               filter(!is.na(percentage_episodes)), episodes, total_episodes)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_beddays_england
#| fig-cap: The percentage of beddays for potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>
                               filter(!is.na(percentage_beddays)),  beddays, total_beddays)

```
:::

#### Standardised rate over time

::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_spells_england
#| fig-cap: Age and sex standardised rate of potentially mitigable admissions in England over the last 9 years. 

england_age_sex_standardised_rates_episodes_total_mitigation<-tar_read(england_age_sex_standardised_rates_episodes_total_mitigation)

plot_of_standardised_rates_over_time(
  england_age_sex_standardised_rates_episodes_total_mitigation)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_beddays_england
#| fig-cap: Age and sex standardised rate of potentially mitigable beddays in England over the last 9 years.

england_age_sex_standardised_rates_beddays_total_mitigation<-tar_read(england_age_sex_standardised_rates_beddays_total_mitigation)

plot_of_standardised_rates_over_time(
  england_age_sex_standardised_rates_beddays_total_mitigation)


```
:::
:::

### ICB

Note: Low numbers of admissions/beddays for Frimley ICB in 2022/23 reflect an issue with data submissions for this period.

::: panel-tabset
#### Number over time

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_spells_icb
#| fig-cap: The number of admissions for all potentially mitigable activity by ICB over the last 9 years. 

number_percentage_over_time_removing_icb_na<-number_percentage_over_time|>
  filter(!is.na(icb_2024_name))


plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
        mutate(activity=episodes),
        'Number')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_spells
#| fig-cap: The percentage change in the number of potentially mitigable admissions by ICB between 2018/19 and 2023/24. 

england_average_numbers_episodes<-calculating_england_average_numbers(number_percentage_over_time, episodes)

plotting_percentage_change_over_time_by_icb(number_percentage_over_time|>filter(!is.na(icb_2024_name)), episodes, icb_2024_name , england_average_numbers_episodes$change, 1.3, 1.3)

```


#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_beddays_icb
#| fig-cap: The number of beddays for all potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
        mutate(activity=beddays), 'Number')
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_beddays
#| fig-cap: The percentage change in the number of potentially mitigable beddays by ICB between 2018/19 and 2023/24. 

england_average_numbers_beddays<-calculating_england_average_numbers(number_percentage_over_time, beddays)


plotting_percentage_change_over_time_by_icb(number_percentage_over_time|>filter(!is.na(icb_2024_name)), beddays, icb_2024_name, england_average_numbers_beddays$change, 1.3, 1.3)

```

:::

#### Crude rate

Total mitigable activity as a percentage of total elective and emergency admissions/beddays.

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_spells_icb
#| fig-cap: The percentage of admissions for potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
            filter(!is.nan(percentage_episodes))|>
        mutate(activity=percentage_episodes), 'Percentage')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_spells
#| fig-cap: The percentage change in the proportion emergency admissions that are for potentially mitigable admissions by ICB between 2018/19 and 2023/24. 

england_average_percentage_episodes<-calculating_england_average_percentage(number_percentage_over_time|>filter(!is.nan(percentage_episodes)), episodes, total_episodes)

plotting_percentage_change_over_time_by_icb(number_percentage_over_time_removing_icb_na, percentage_episodes, icb_2024_name, england_average_percentage_episodes$change, 2.3, 1.3)


```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_beddays_icb
#| fig-cap: The percentage of beddays for potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
              filter(!is.nan(percentage_beddays))|>
        mutate(activity=percentage_beddays), 'Percentage')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_beddays
#| fig-cap: The percentage change in the proportion emergency beddays that are for potentially mitigable beddays by ICB between 2018/19 and 2023/24. 

england_average_percentage_beddays<-calculating_england_average_percentage(number_percentage_over_time|>filter(!is.nan(percentage_episodes)), beddays, total_beddays)

plotting_percentage_change_over_time_by_icb(number_percentage_over_time_removing_icb_na, percentage_beddays, icb_2024_name, england_average_percentage_beddays$change,  1.6, 1.3)

```
:::

#### Standardised rate over time

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_spells_icb
#| fig-cap: Age and sex standardised rate of potentially mitigable admissions by ICB over the last 9 years. 

icb_age_sex_standardised_rates_episodes_total_mitigation<-tar_read(icb_age_sex_standardised_rates_episodes_total_mitigation)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_episodes_total_mitigation|> 
     mutate(activity=value)),
  'Standardised rate per 100,000')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_spells
#| fig-cap: The percentage change in the standardised rate of potentially mitigable admissions by ICB between 2018/19 and 2023/24. 

england_average_standardised_episodes_total_mitigation<-calculating_england_average_standardised(england_age_sex_standardised_rates_episodes_total_mitigation)

plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_episodes_total_mitigation, value, icb_2024_name, england_average_standardised_episodes_total_mitigation$change, 1.3, 1.2)

```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_beddays_icb
#| fig-cap: Age and sex standardised rate of potentially mitigable beddays by ICB over the last 9 years.

icb_age_sex_standardised_rates_beddays_total_mitigation<-tar_read(icb_age_sex_standardised_rates_beddays_total_mitigation)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_beddays_total_mitigation|> 
     mutate(activity=value)),
  'Standardised rate per 100,000')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_beddays
#| fig-cap: The percentage change in the standardised rate of potentially mitigable beddays by ICB between 2018/19 and 2023/24. 


england_average_standardised_beddays_total_mitigation<-calculating_england_average_standardised(england_age_sex_standardised_rates_beddays_total_mitigation)

plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_beddays_total_mitigation, value,icb_2024_name, england_average_standardised_beddays_total_mitigation$change, 1.3, 1.3)


```
:::
:::

### Change in age and sex standardised rate over time relative to level of activity

This chart shows the percentage change for each ICB relative to it's starting level of admissions/beddays to help demonstrate performance across ICBs. Those ICBs in the lower left quadrant (shaded in green) could be considered as performing well; they already had relatively low standardised rates of admissions/beddays in 2018/19 and have continued to make further decreases over the last five years.


::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_episodes
#| fig-cap: The standardised rate of potentially mitigable admissions (in 2018/19) versus the percentage change in admissions between 2018/19 and 2023/24 for ICBs. 

plotting_total_activity_vs_percentage_change(icb_age_sex_standardised_rates_episodes_total_mitigation, value)


```
#### Beddays

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_beddays
#| fig-cap: The standardised rate of potentially mitigable beddays (in 2018/19) versus the percentage change in beddays between 2018/19 and 2023/24 for ICBs. 
#| 
plotting_total_activity_vs_percentage_change(icb_age_sex_standardised_rates_beddays_total_mitigation, value)


```

:::




