# Summary of total mitigation {#sec-summary .unnumbered}

```{r}
library("flextable")
library("tidyr")
library("dplyr")
library("ggplot2")
library("StrategyUnitTheme")
library("forcats")
library("ComplexUpset")
library("scales")
library("targets")
library("plotly")
library("patchwork")
library("readxl")
library("ggVennDiagram")
library("stringr")

source("R/captions.R")
source("R/general.R")
source("R/descriptive_analyses.R")
source("R/comparative_analyses.R")
source("R/Functions for cohort overlap.R")
source("R/Functions for trend analysis.R")

options(scipen = 999)

numbers_over_time<-tar_read(numbers_over_time)
numbers_over_time_total_mitigation<-targets::tar_read(numbers_over_time_total_mitigation)|>
  filter(fyear>"201415")
total_cohort_numbers_2324<-tar_read(total_cohort_numbers_2324)
icb_population_data<-tar_read(icb_population_data)
denominator_over_time<-tar_read(denominator_over_time)
england_age_sex_standardised_rates_beddays_total_mitigation<-tar_read(england_age_sex_standardised_rates_beddays_total_mitigation)
england_age_sex_standardised_rates_episodes_total_mitigation<-tar_read(england_age_sex_standardised_rates_episodes_total_mitigation)
```

```{r global variables}
cohort <- "all"
cohort_title <- "All Mitigation"
treatment_type <- "both"
treatment_type_title <- format_treatment_for_caption(treatment_type)
```

```{r}
number_percentage_over_time<-numbers_over_time_total_mitigation|>
  left_join(denominator_over_time, by=c("age_range", "sex", "year", "icb", "icb_2024_name"))|>
  summarise(episodes=sum(episodes, na.rm=TRUE),
            beddays=sum(beddays, na.rm=TRUE),
            total_episodes=sum(total_episodes_all, na.rm=TRUE),
            total_beddays=sum(total_beddays_all, na.rm=TRUE),
            .by=c(icb, icb_2024_name, year))|>
  filter(year!="2014/15")|>
  mutate(percentage_episodes=round((episodes/total_episodes)*100,1),
         percentage_beddays=round((beddays/total_beddays)*100,1))|>
  as.data.frame()
```

## Mitigators included in this analysis

The numbers of admissions and beddays give the potentially mitigable activity for England in 2023/24.

The mitigators are divided into 4 groups according to the mechanism by which mitigation could occur:

-   Redirection/Substitution
-   Prevention
-   Relocation
-   Efficiencies

Redirection/Substitution, Prevention and Relocation mitigators will affect the number of admissions and will also therefore impact the number of beddays.

Efficiency mitigators are focused on reducing length of stay and will therefore only impact the number of beddays.

Virtual Ward mitigators are considered both a Relocation mitigator and an Efficiency mitigator.

```{r, fig.height=8, fig.width=10}

mitigator_summary_table<-read_excel("summary_mitigators_table.xlsx")|>
  left_join(numbers_over_time|>
              filter(year=="2023/24")|>
              summarise(episodes=sum(episodes),
                        beddays=sum(beddays),
                        .by=cohorts), by=c("mitigator_code"="cohorts"))|>
  select(-activity_group, -mitigator_code)|>
    mutate(episodes=ifelse(mechanism=="Efficiencies", NA, episodes))|>
  rename(`Mechanism of mitigation`=mechanism)


mitigator_summary_table|>
  as_grouped_data(groups = "Mechanism of mitigation")|>
  as_flextable() |>
    set_header_labels(mitigator_name="Mitigator name",
                      type_of_admission="Type of admission",
                      episodes="Admissions",
                      beddays="Beddays")|>
    align(part = "header", align = "left") |>
    bg(bg = "#f9bf07", part = "header") |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Redirection/Substitution") |>
        bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Redirection/Substitution",
        bg="#D8DBDC" ) |>
      bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Prevention",
        bg="#D8DBDC" ) |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Prevention") |>
      bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies",
        bg="#D8DBDC") |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies") |>
       bg( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies & Relocation",
        bg="#D8DBDC") |>
    bold( part = "body",
         i = ~ `Mechanism of mitigation` == "Efficiencies & Relocation") |>
    bold(bold = TRUE, part = "header") |>
    fontsize(size = 10, part = "body") |>
    fontsize(size = 11, part = "header") |>
    padding(padding = 2,
            part = "all",
            padding.top = NULL) |>
    autofit()
  

```

NOTE: The sum of all the individual mitigator activity in this table does not add up to the total potential mitigable activity. This is because much of the activity is included within multiple different mitigator cohorts and thus adding the total for each mitigator will lead to double counting of admissions and beddays.

#### Number of admissions and beddays for each mechanism of mitigation

```{r}
total_cohort_numbers_2324|>
  generate_data_for_mechanism_cohort_overlaps()|>
  gather(key=mechanism, value=value, -episodes, -beddays)|>
  filter(value!=0)|>
  summarise(episodes=sum(episodes),
            beddays=sum(beddays),
                        .by=mechanism) |>
  mutate(episodes=ifelse(mechanism=="Efficiencies", NA, episodes))|>
  flextable() |>
    set_header_labels(episodes="Admissions",
                      beddays="Beddays",
                      mechanism="Mechanism of mitgation")|>
    align(part = "header", align = "left") |>
    bg(bg = "#f9bf07", part = "header") |>
    bold(bold = TRUE, part = "header") |>
    fontsize(size = 10, part = "body") |>
    fontsize(size = 11, part = "header") |>
    padding(padding = 2,
            part = "all",
            padding.top = NULL) |>
    autofit()
  

```

NOTE: As with the previous table the sum of all the admissions and beddays does not add up to the total potential mitigable activity, as much of the activity is included within more than one mechanism of mitigation group and and thus adding the numbers for each group will lead to double counting.

## Potential mitigable activity for England in 2023/24

```{r}
total_mitigator_activity<-numbers_over_time_total_mitigation|>
  filter(year=="2023/24")|>
  summarise(episodes=sum(episodes),
            beddays=sum(beddays))

```

In 2023/24 in England there were **`r format(total_mitigator_activity$episodes, big.mark=",")` admissions** and **`r format(total_mitigator_activity$beddays, big.mark=",")` beddays** for potentially mitigable activity. This total excludes any double counting as a result of activity being including in multiple mitigator cohorts.

## Overlap between the mechanism of mitigation groups

Many admissions meet the criteria to be included in more than one mechanism of mitigation group. Since these potential mechanism of mitigation groups are not mutually exclusive there is a need to understand which groups overlap and the degree of overlap between the cohorts.


:::panel-tabset

#### Admissions

::: columns
::: {.column width="70%"}
```{r, fig.width=4, fig.height=4}
#| label: fig-overlap_mechanism_cohorts_episodes
#| fig-cap: Venn diagram showing the overlap in admissions between the mechanisms of mitigation groups.

total_cohort_numbers_2324<-tar_read(total_cohort_numbers_2324)

#generate_venn_diagram(total_cohort_numbers_2324, episodes)

```
:::

::: {.column width="30%"}
```{r, fig.width=3, fig.height=4}
#| label: fig-number_of_mechanism_groups_episodes
#| fig-cap: Number of mechanism groups the admissions are a part of.

plotting_barchart_number_of_mechanism_groups(total_cohort_numbers_2324, episodes)

```
:::

NB: Efficiency mitigators do not impact the number of admissions, only the length of stay, hence they do not overlap in terms of admissions with the other cohorts.
:::

The majority of mitigable admissions (59%) are purely for activity that could be prevented. 

Overall three quarters of mitigable admissions fall into just one mechanism of mitigation group.

#### Beddays

::: columns
::: {.column width="70%"}
```{r, fig.width=7, fig.height=4}
#| label: fig-overlap_mechanism_cohorts_beddays
#| fig-cap: Venn diagram showing the overlap in beddays between the mechanisms of mitigation groups.

#generate_venn_diagram(total_cohort_numbers_2324, beddays)

```
:::

::: {.column width="30%"}
```{r, fig.width=3, fig.height=4}
#| label: fig-number_of_mechanism_groups_beddays
#| fig-cap: Number of mechanism groups the beddays are a part of.

plotting_barchart_number_of_mechanism_groups(total_cohort_numbers_2324, beddays)

```
:::
:::

The majority of mitigable beddays are included in multiple mechanism of mitigation groups, just over a quarter of mitgable beddays are within a single mechanism group. 

One third of mitigable beddays are included with 3 mechanism of mitigation groups (Redirection/Substitution, Prevention and Efficiencies)

:::
## Comparative Analysis

::: panel-tabset
### Admissions

::: panel-tabset
#### Integrated Care Board

```{r}
#| output: false
summary_icb_admissions_all <- targets::tar_read(summary_icb_admissions_all)

icb_23_shp <- sf::st_read("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Integrated_Care_Boards_April_2023_EN_BGC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") |>
  janitor::clean_names() |>
  dplyr::mutate(icb23nm = simplify_icb_name(icb23nm))

number_icb_admissions_all_map <- summary_icb_admissions_all |>
  get_summary_by_icb_map(icb_23_shp, "total_count")

perc_icb_admissions_all_map <- summary_icb_admissions_all |>
  get_summary_by_icb_map(icb_23_shp, "perc")

rate_icb_admissions_all_map <- summary_icb_admissions_all |>
  get_summary_by_icb_map(icb_23_shp, "value")
```

::: panel-tabset
##### Number of admissions

::: panel-tabset
###### Bars

```{r}
#| label: fig-number_icb_admissions_all_bar
#| fig-cap: !expr get_caption_by_icb(cohort_title, "number", "admissions")
england_value <- get_england_value(
  "total_count", 
  data = summary_icb_admissions_all)

get_summary_by_icb_bar(
  summary_icb_admissions_all, 
  "total_count", 
  cohort,
  england_value)

rm(england_value)
```

###### Map

```{r}
#| label: fig-number_icb_admissions_all_map
#| fig-cap: !expr get_caption_by_icb(cohort_title, "number", "admissions")
number_icb_admissions_all_map
```
:::

##### Percentage of `r treatment_type_title` activity

::: panel-tabset
###### Bars

```{r}
#| label: fig-perc_icb_admissions_all_bar
#| fig-cap: !expr get_caption_by_icb(cohort_title, "perc", "admissions", treatment_type)
total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

england_value <- get_england_value(
  "perc_total_mitigation",
  activity = "admissions",
  treatment = treatment_type,
  data = number_percentage_over_time)

get_summary_by_icb_bar(
  summary_icb_admissions_all, 
  "perc", 
  cohort,
  england_value)

rm(england_value)
```

###### Map

```{r}
#| label: fig-perc_icb_admissions_all_map
#| fig-cap: !expr get_caption_by_icb(cohort_title, "perc", "admissions", treatment_type)
perc_icb_admissions_all_map
```
:::

##### Age and sex standardised rates per 100,000 population

::: panel-tabset
###### Bars

```{r}
#| label: fig-rate_icb_admissions_all_bar
#| fig-cap: !expr get_caption_by_icb(cohort_title, "SR", "admissions")
england_value <- get_england_value(
  "value",
  data = england_age_sex_standardised_rates_episodes_total_mitigation,
  cohort = cohort)

get_summary_by_icb_bar(
  summary_icb_admissions_all, 
  "value", 
  cohort,
  england_value)

rm(england_value)
```

###### Map

```{r}
#| label: fig-rate_icb_admissions_all_map
#| fig-cap: !expr get_caption_by_icb(cohort_title, "SR", "admissions")
rate_icb_admissions_all_map
```
:::

##### Table

```{r}
#| label: tbl-rate_icb_admissions_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "admissions", treatment_type, "icb")
get_summary_by_geography_table(
  summary_icb_admissions_all,
  "episodes", 
  treatment_type)
```
:::

#### Local Authority

```{r}
#| label: tbl-rate_la_admissions_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "admissions", treatment_type, "la")
targets::tar_read(summary_la_admissions_all) |>
  get_summary_by_geography_table("episodes",
                                 treatment_type)
```
:::

### Beddays

::: panel-tabset
#### Integrated Care Board

```{r}
#| output: false
summary_icb_beddays_all <- targets::tar_read(summary_icb_beddays_all)

number_icb_beddays_all_map <- summary_icb_beddays_all |>
  get_summary_by_icb_map(icb_23_shp, "total_count")

perc_icb_beddays_all_map <- summary_icb_beddays_all |>
  get_summary_by_icb_map(icb_23_shp, "perc")

rate_icb_beddays_all_map <- summary_icb_beddays_all |>
  get_summary_by_icb_map(icb_23_shp, "value")
```

::: panel-tabset
##### Number of beddays

::: panel-tabset
###### Bars

```{r}
#| label: fig-number_icb_beddays_all_bar
#| fig-cap: !expr get_caption_by_icb(cohort_title, "number", "beddays")
england_value <- get_england_value(
  "total_count", 
  data = summary_icb_beddays_all)

get_summary_by_icb_bar(
  summary_icb_beddays_all, 
  "total_count", 
  cohort,
  england_value)

rm(england_value)
```

###### Map

```{r}
#| label: fig-number_icb_beddays_all_map
#| fig-cap: !expr get_caption_by_icb(cohort_title, "number", "beddays")
number_icb_beddays_all_map
```
:::

##### Percentage of `r treatment_type_title` activity

::: panel-tabset
###### Bars

```{r}
#| label: fig-perc_icb_beddays_all_bar
#| fig-cap: !expr get_caption_by_icb(cohort_title, "perc", "beddays", treatment_type)
total_beddays_admissions <- targets::tar_read(total_beddays_admissions)

england_value <- get_england_value(
  "perc_total_mitigation",
  activity = "beddays",
  treatment = treatment_type,
  data = number_percentage_over_time)

get_summary_by_icb_bar(
  summary_icb_beddays_all,
  "perc",
  cohort,
  england_value)

rm(england_value)
```

###### Map

```{r}
#| label: fig-perc_icb_beddays_all_map
#| fig-cap: !expr get_caption_by_icb(cohort_title, "perc", "beddays", treatment_type)
perc_icb_beddays_all_map
```
:::

##### Age and sex standardised rates per 100,000 population

::: panel-tabset
###### Bars

```{r}
#| label: fig-rate_icb_beddays_all_bar
#| fig-cap: !expr get_caption_by_icb(cohort_title, "SR", "beddays")
england_value <- get_england_value(
  "value",
  data = england_age_sex_standardised_rates_beddays_total_mitigation,
  cohort = cohort)

get_summary_by_icb_bar(
  summary_icb_beddays_all,
  "value",
  cohort,
  england_value)

rm(england_value)
```

###### Map

```{r}
#| label: fig-rate_icb_beddays_all_map
#| fig-cap: !expr get_caption_by_icb(cohort_title, "SR", "beddays")
rate_icb_beddays_all_map
```
:::

##### Table

```{r}
#| label: tbl-rate_icb_beddays_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "beddays", treatment_type, "icb")
get_summary_by_geography_table(
  summary_icb_beddays_all, 
  "beddays", 
  treatment_type)
```
:::

#### Local Authority

```{r}
#| label: tbl-rate_la_beddays_all
#| tbl-cap: !expr get_caption_by_geography_table(cohort_title, "beddays", treatment_type, "la")
targets::tar_read(summary_la_beddays_all) |>
  get_summary_by_geography_table("beddays", treatment_type)
```
:::
:::
## Trend Analysis

We aim to understand whether there have been decreases, or increases, in potentially mitigable activity over time. We have considered total mitigable admissions and beddays over the past 9 years in England as a whole and for each ICB, including:

a\) the absolute number of admissions/beddays,

b\) the crude rate of admissions/beddays (i.e. as proportion of total admissions),

c\) the age and sex standardised rates of these admissions/beddays using the England 2021 census population.

To help understand the variability between ICBs we have calculated for each ICB the percentage change between 2018/19 and 2023/24.

### England

::: panel-tabset
#### Number over time

```{r}
# England average numbers and % change
england_average_numbers_episodes<-calculating_england_average_numbers(number_percentage_over_time, episodes)

england_average_numbers_beddays<-calculating_england_average_numbers(number_percentage_over_time, beddays)

# England average percentages and % change
england_average_percentage_beddays<-calculating_england_average_percentage(number_percentage_over_time|>filter(!is.nan(percentage_episodes)), beddays, total_beddays)

england_average_percentage_episodes<-calculating_england_average_percentage(number_percentage_over_time|>filter(!is.nan(percentage_episodes)), episodes, total_episodes)


# England standardised rate and % change
england_average_standardised_episodes_total_mitigation<-calculating_england_average_standardised(england_age_sex_standardised_rates_episodes_total_mitigation)


england_average_standardised_beddays_total_mitigation<-calculating_england_average_standardised(england_age_sex_standardised_rates_beddays_total_mitigation)

```

Over the last 5 years (2018/19 to 2023/24), there has been a `r england_average_numbers_episodes$change` % in the percentage of admissions that are for potentially mitigable activity and a `r england_average_numbers_beddays$change` % increase in the percentage of beddays that are for potentially mitigable activity.

::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_spells_england_all_mitigators
#| fig-cap: The number of admissions for all mitigable activity in England over the last 9 years.

plot_of_number_over_time(number_percentage_over_time, episodes)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-number_trends_beddays_england_all_mitigators
#| fig-cap: The number of beddays for all mitigable activity cohort in England over the last 9 years. 
plot_of_number_over_time(number_percentage_over_time,  beddays)

```
:::

#### Percentage of total admissions

Total mitigable activity as a percentage of total activity (elective and emergency admissions/beddays).

Over the last 5 years (2018/19 to 2023/24), there has been a `r england_average_percentage_episodes$change` % increase in potentially mitigable admissions and a `r england_average_percentage_beddays$change` % increase in potentially mitigable beddays.

::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_spells_england
#| fig-cap: The percentage of admissions for potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>          filter(!is.na(percentage_episodes)), episodes, total_episodes)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-percent_trends_beddays_england
#| fig-cap: The percentage of beddays for potentially mitigable activity in England over the last 9 years. 

plot_of_percentage_over_time(number_percentage_over_time|>
                               filter(!is.na(percentage_beddays)),  beddays, total_beddays)

```
:::

#### Standardised rate over time

Over the last 5 years (2018/19 to 2023/24), when accounting for changes in the population age and sex, there has been a `r england_average_standardised_episodes_total_mitigation$change` % increase in potentially mitigable admissions. However, there has been a `r england_average_standardised_beddays_total_mitigation$change` % decrease in potentially mitigable beddays, suggesting reduced length of stays for mitigable activity.


::: panel-tabset
#### Admissions

```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_spells_england
#| fig-cap: Age and sex standardised rate of potentially mitigable admissions in England over the last 9 years. 


plot_of_standardised_rates_over_time(
  england_age_sex_standardised_rates_episodes_total_mitigation)

```

#### Beddays

```{r, fig.width=7, fig.height=3}
#| label: fig-stardardised_trends_beddays_england
#| fig-cap: Age and sex standardised rate of potentially mitigable beddays in England over the last 9 years.

plot_of_standardised_rates_over_time(
  england_age_sex_standardised_rates_beddays_total_mitigation)

```
:::
:::

### ICB

Total potentially mitigable activity over time is shown for each ICB to demonstrate the patterns of change and the degree of variability between ICBs over time. The percentage change in total potentially mitigable activity between 2018/19 and 2023/24 is compared across ICBs and shown relative to the England average. 

Note: Low numbers of admissions/beddays for Frimley ICB in 2022/23 reflect an issue with data submissions for this period.

::: panel-tabset
#### Number over time

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_spells_icb
#| fig-cap: The number of admissions for all potentially mitigable activity by ICB over the last 9 years. 

number_percentage_over_time_removing_icb_na<-number_percentage_over_time|>
  filter(!is.na(icb_2024_name))


plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
        mutate(activity=episodes),
        'Number')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_spells
#| fig-cap: The percentage change in the number of potentially mitigable admissions by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(number_percentage_over_time|>filter(!is.na(icb_2024_name)), episodes, icb_2024_name , england_average_numbers_episodes$change, 1.3, 1.3)

```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_beddays_icb
#| fig-cap: The number of beddays for all potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
        mutate(activity=beddays), 'Number')
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_beddays
#| fig-cap: The percentage change in the number of potentially mitigable beddays by ICB between 2018/19 and 2023/24. 

plotting_percentage_change_over_time_by_icb(number_percentage_over_time|>filter(!is.na(icb_2024_name)), beddays, icb_2024_name, england_average_numbers_beddays$change, 1.3, 1.3)

```
:::

#### Percentage of total admissions

Total mitigable activity as a percentage of total elective and emergency admissions/beddays.

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_spells_icb
#| fig-cap: The percentage of admissions for potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
            filter(!is.nan(percentage_episodes))|>
        mutate(activity=percentage_episodes), 'Percentage')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_spells
#| fig-cap: The percentage change in the proportion emergency admissions that are for potentially mitigable admissions by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(number_percentage_over_time_removing_icb_na, percentage_episodes, icb_2024_name, england_average_percentage_episodes$change, 2.3, 1.3)


```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_beddays_icb
#| fig-cap: The percentage of beddays for potentially mitigable activity by ICB over the last 9 years. 

plotting_icb_over_time(number_percentage_over_time_removing_icb_na|>
              filter(!is.nan(percentage_beddays))|>
        mutate(activity=percentage_beddays), 'Percentage')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_beddays
#| fig-cap: The percentage change in the proportion emergency beddays that are for potentially mitigable beddays by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(number_percentage_over_time_removing_icb_na, percentage_beddays, icb_2024_name, england_average_percentage_beddays$change,  1.6, 1.3)

```
:::

#### Standardised rate over time

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_spells_icb
#| fig-cap: Age and sex standardised rate of potentially mitigable admissions by ICB over the last 9 years. 

icb_age_sex_standardised_rates_episodes_total_mitigation<-tar_read(icb_age_sex_standardised_rates_episodes_total_mitigation)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_episodes_total_mitigation|> 
     mutate(activity=value)),
  'Standardised rate per 100,000')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_spells
#| fig-cap: The percentage change in the standardised rate of potentially mitigable admissions by ICB between 2018/19 and 2023/24. 


plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_episodes_total_mitigation, value, icb_2024_name, england_average_standardised_episodes_total_mitigation$change, 1.3, 1.2)

```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_beddays_icb
#| fig-cap: Age and sex standardised rate of potentially mitigable beddays by ICB over the last 9 years.

icb_age_sex_standardised_rates_beddays_total_mitigation<-tar_read(icb_age_sex_standardised_rates_beddays_total_mitigation)

plotting_icb_over_time(
  (icb_age_sex_standardised_rates_beddays_total_mitigation|> 
     mutate(activity=value)),
  'Standardised rate per 100,000')

```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_beddays
#| fig-cap: The percentage change in the standardised rate of potentially mitigable beddays by ICB between 2018/19 and 2023/24. 

plotting_percentage_change_over_time_by_icb(icb_age_sex_standardised_rates_beddays_total_mitigation, value,icb_2024_name, england_average_standardised_beddays_total_mitigation$change, 1.3, 1.3)


```
:::
:::

### Change in age and sex standardised rate over time relative to level of activity

This chart shows the percentage change for each ICB (between 2018/19 and 2023/24) relative to it's starting level of admissions/beddays (in 2018/19) to help demonstrate performance across ICBs. 

Those ICBs in the lower left quadrant (shaded in green) could be considered as performing well; they already had relatively low standardised rates of admissions/beddays in 2018/19 and have continued to make further decreases over the last five years.

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_episodes
#| fig-cap: The standardised rate of potentially mitigable admissions (in 2018/19) versus the percentage change in admissions between 2018/19 and 2023/24 for ICBs. 

plotting_total_activity_vs_percentage_change(icb_age_sex_standardised_rates_episodes_total_mitigation, value)


```

#### Beddays

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_beddays
#| fig-cap: The standardised rate of potentially mitigable beddays (in 2018/19) versus the percentage change in beddays between 2018/19 and 2023/24 for ICBs. 
#| 
plotting_total_activity_vs_percentage_change(icb_age_sex_standardised_rates_beddays_total_mitigation, value)


```
:::
