This analysis is to explore how potentially mitigable activity for the `r cohort_title` `r cohort_group` varies by Integrated Care Board and Local Authority.

### Integrated Care Board

```{r}
#| output: asis
knitr::knit_child(
                  input = "child-dir/_child-comparative_icb.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

### Local Authority

To explore how potentially mitigable activity may vary between Local Authority (LA) the table below contains the number, percentage and age and sex standardised rates per 100,000 population of mitigable activity by LA. Columns in the table can be ordered and specific LAs can be searched for.

```{r}
#| output: asis
geography <- "la"

knitr::knit_child(
                  input = "child-dir/_child-comparative_local-authority.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```

### Acute Provider

The table below contains the number, percentage and age and sex standardised rates per 100,000 population of mitigable activity by acute NHS providers. Columns in the table can be ordered and specific providers and the ICB system that the providers are aligned with can be searched for.

```{r}
#| output: asis
geography <- "provider"

knitr::knit_child(
                  input = "child-dir/_child-comparative_local-authority.qmd",
                  envir = environment(),
                  quiet = TRUE
                ) |>
                  cat(sep = '\n')
```