```{r}
icb_age_sex_standardised_rates_episodes <- tar_read(icb_age_sex_standardised_rates_episodes)

icb_age_sex_standardised_rates_beddays <- tar_read(icb_age_sex_standardised_rates_beddays)
```

::: panel-tabset
#### Number over time

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_spells_icb
#| fig-cap: !expr get_caption_trends(cohort_title, "number", "admissions", "icb") 
plotting_icb_over_time(number_percentage_over_time |>
                         mutate(activity = episodes),
                       'Number')
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_spells
#| fig-cap: !expr get_caption_trends_percentage_change(cohort_title, "number", "admissions")

england_average_numbers_episodes <- calculating_england_average_numbers(number_percentage_over_time, episodes)

plotting_percentage_change_over_time_by_icb(
  number_percentage_over_time |> filter(!is.na(icb_2024_name)),
  episodes,
  icb_2024_name ,
  england_average_numbers_episodes$change,
  1.6,
  1.3
)
```


#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-number_trends_beddays_icb
#| fig-cap: !expr get_caption_trends(cohort_title, "number", "beddays", "icb")
plotting_icb_over_time(number_percentage_over_time |>
                         mutate(activity = beddays),
                       'Number')
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_number_beddays
#| fig-cap: !expr get_caption_trends_percentage_change(cohort_title, "number", "beddays") 

england_average_numbers_beddays <- calculating_england_average_numbers(number_percentage_over_time, beddays)

plotting_percentage_change_over_time_by_icb(
  number_percentage_over_time |> filter(!is.na(icb_2024_name)),
  beddays,
  icb_2024_name,
  england_average_numbers_beddays$change,
  1.6,
  1.3
)
```

:::

#### Percentage of `r treatment_type_title` activity

`r cohort_title` as a percentage of `r treatment_type_title` activity.

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_spells_icb
#| fig-cap: !expr get_caption_trends(cohort_title, "percentage", "admissions", "icb")
plotting_icb_over_time(
  number_percentage_over_time |>
    mutate(activity = percentage_episodes) |>
    filter(!is.na(activity)),
  'Percentage'
)
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_spells
#| fig-cap: !expr get_caption_trends_percentage_change(cohort_title, "prop", "admissions", treatment_type) 

england_average_percentage_episodes <- calculating_england_average_percentage(
  number_percentage_over_time |> 
    filter(!is.na(total_episodes)),
  episodes,
  total_episodes)

plotting_percentage_change_over_time_by_icb(
  number_percentage_over_time |> filter(!is.na(icb_2024_name)),
  percentage_episodes,
  icb_2024_name,
  england_average_percentage_episodes$change,
  1.6,
  1.3
)
```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-percent_trends_beddays_icb
#| fig-cap: !expr get_caption_trends(cohort_title, "percentage", "beddays", "icb")
plotting_icb_over_time(
  number_percentage_over_time |>
    mutate(activity = percentage_beddays) |>
    filter(!is.na(activity)),
  'Percentage'
)
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_percent_beddays
#| fig-cap: !expr get_caption_trends_percentage_change(cohort_title, "prop", "beddays", treatment_type) 

england_average_percentage_beddays <- calculating_england_average_percentage(
  number_percentage_over_time |>
    filter(!is.na(percentage_beddays)),
  beddays,
  total_beddays)

plotting_percentage_change_over_time_by_icb(
  number_percentage_over_time |> filter(!is.na(icb_2024_name)),
  percentage_beddays,
  icb_2024_name,
  england_average_percentage_beddays$change,
  1.6,
  1.3
)
```
:::

#### Age and sex standardised rates over time

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_spells_icb
#| fig-cap: !expr get_caption_trends(cohort_title, "SR", "admissions", "icb")
plotting_icb_over_time(
  (icb_age_sex_standardised_rates_episodes |>
      filter(cohorts == cohort) |>
      mutate(activity = value)
  ),
  'Standardised rate per 100,000'
)
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_spells
#| fig-cap: !expr get_caption_trends_percentage_change(cohort_title, "SR", "admissions") 

england_average_standardised_episodes <- calculating_england_average_standardised(england_age_sex_standardised_rates_episodes)

plotting_percentage_change_over_time_by_icb(
  icb_age_sex_standardised_rates_episodes |>
    filter(cohorts == cohort),
  value,
  icb_2024_name,
  england_average_standardised_episodes$change,
  1.6,
  1.7
)
```

#### Beddays

```{r, fig.width=5, fig.height=3}
#| label: fig-stardardised_trends_beddays_icb
#| fig-cap: !expr get_caption_trends(cohort_title, "SR", "beddays", "icb")
plotting_icb_over_time(
  (icb_age_sex_standardised_rates_beddays |>
      filter(cohorts == cohort) |>
      mutate(activity = value)
  ),
  'Standardised rate per 100,000'
)
```

<br>

```{r, fig.height=6, fig.width=8}
#| label: fig-percent_change_standardised_beddays
#| fig-cap: !expr get_caption_trends_percentage_change(cohort_title, "SR", "beddays") 
england_average_standardised_beddays <- calculating_england_average_standardised(england_age_sex_standardised_rates_beddays)

plotting_percentage_change_over_time_by_icb(
  icb_age_sex_standardised_rates_beddays |>
    filter(cohorts == cohort),
  value,
  icb_2024_name,
  england_average_standardised_beddays$change,
  1.6,
  1.6
)
```
:::
:::

#### Change in age and sex standardised rate over time relative to level of activity by ICB

This chart shows the percentage change for each ICB relative to it's starting level of admissions/beddays to help demonstrate performance across ICBs. Those ICBs in the lower left quadrant (shaded in green) could be considered as performing well; they already had relatively low standardised rates of admissions/beddays in 2018/19 and have continued to make further decreases over the last five years.

::: panel-tabset
#### Admissions

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_episodes_icb
#| fig-cap: !expr get_caption_activity_vs_perc_change(cohort_title, "admissions") 
plotting_total_activity_vs_percentage_change(
  icb_age_sex_standardised_rates_episodes, 
  icb_2024_name)
```
#### Beddays

```{r, fig.width=5, fig.height=4}
#| label: fig-activity_vs_rate_of_change_beddays_icb
#| fig-cap: !expr get_caption_activity_vs_perc_change(cohort_title, "beddays")
plotting_total_activity_vs_percentage_change(
  icb_age_sex_standardised_rates_beddays, 
  icb_2024_name)
```

:::
